---
title: "GDP Colorpleth Map of Europe"
author: "John Hios"
date: "16/06/2022"
output: html_notebook
---

<br>
__Library calls__
```{r}
library(here)
library(tidyverse)
library(janitor)
```


<br>
__Read cleaned data__
```{r}
source(here("scripts/clean_gdp_data.R"))
```

<br>
__OECD Data: Gross Domestic Product (GDP)__

Select the GDP data (million USD) of UK and other European countries for year 2018 (K-means clustering is performed for 2018, too) and calculate their share of total Europe's GDP
```{r}
gdp_europe <- gdp %>%
  mutate(year = year(year)) %>%
  filter(
    country %in% c("AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", 
                   "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", 
                   "LUX", "MLT", "NLD", "NOR", "POL", "PRT", "ROU", "SVK", "SVN", 
                   "ESP", "SWE", "CHE", "GBR", "RUS", "ALB", "SRB", "MKD"),
    year == 2018
    ) %>%
  mutate(country = recode(country,
    "AUT" = "Austria", "BEL" = "Belgium", "BGR" = "Bulgaria", "HRV" = "Croatia", "CYP" = "Cyprus",
    "CZE" = "Czech Republic", "DNK" = "Denmark", "EST" = "Estonia", "FIN" = "Finland", 
    "FRA" = "France", "DEU" = "Germany", "GRC" = "Greece", "HUN" = "Hungary", "IRL" = "Ireland",
    "ITA" = "Italy", "LVA" = "Latvia", "LTU"= "Lithuania", "LUX" = "Luxembourg", "MLT" = "Malta",
    "NLD" = "Netherlands", "NOR" = "Norway", "POL" = "Poland", "PRT" = "Portugal", 
    "ROU" = "Romania", "SVK" = "Slovakia", "SVN" = "Slovenia", "ESP" = "Spain" , "SWE" = "Sweden", 
    "CHE" = "Switzerland", "GBR" = "UK", "RUS" = "Russia", "ALB" = "Albania", "SRB" = "Serbia", 
    "MKD" = "North Macedonia"
  )) %>% 
  mutate(gdp_pc = gdp_mln_usd/sum(gdp_mln_usd)*100)
  
```



<br>
Retrieve the world map data:
```{r}
euromapdata <- map_data("world")
glimpse(euromapdata)
```

Check for NA values:
```{r}
euromapdata %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


Left join world map data with European country GDP data 
```{r}
euromapdata <- euromapdata %>%
  left_join(gdp_europe, by = c("region" = "country")) 
```



```{r}
euromapdata %>% 
  ggplot(aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = gdp_pc), color = "black") +
  coord_sf(xlim = c(-13,35), ylim = c(34,72), expand = FALSE) +
  theme_void() +
  theme(panel.background = element_blank()) +
  scale_fill_steps(n.breaks = 4, na.value = "lightgrey") +
  ggtitle(
    "European countries by share of total Europe's GDP",
    subtitle = "(OECD data for 2018)") +
  labs(fill = "GDP share (%)")

```

```{r}
gdp_europe %>% 
  arrange(desc(gdp_pc))
```

The UK economy is very similar in size with France's economy. 

Germany, France and the UK have comparable economies and population size. Therefore France and to a lesser extent Germany can serve as a basis of comparison.








 







