---
title: "R Notebook"
output: html_notebook
---

<br>
__Library calls__
```{r}
library(here)
```

<br>
__Read cleaned data__
```{r}
source(here("scripts/clean_gdp_phw_data.R"))
source(here("scripts/clean_inv_asset_data.R"))
source(here("scripts/clean_gfcf_data.R"))
source(here("scripts/clean_edu_exp_data.R"))
source(here("scripts/clean_gdp_data.R"))
source(here("scripts/clean_productivity_phw_data.R"))
```

<br>
__View GDP per hour worked data (productivity)__

View G-7 cross-country GDP per hour worked time-series
```{r}
gdp_phw %>% 
  select(-c(indicator, subject, frequency, flag_codes)) %>% 
  filter(
    country %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "USD"
  ) %>% 
  ggplot() +
  aes(x = year, y = value, colour = country) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "G-7 cross country GDP per hour worked",
    subtitle =  "indicator is measured in USD (constant prices 2010 and PPPs)"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP per hour worked ($) \n",
    colour = "Country"
  ) 
  
```


View cross country GDP per hour worked for 2020 (constant prices)
```{r}
gdp_phw %>% 
  mutate(year = year(year)) %>% 
  filter(
    measure == "USD",
    year == 2020
  ) %>%  
  select(-c(indicator, frequency, measure, subject, year, flag_codes)) %>%  
  ggplot() +
  aes(
    x = reorder(country, value), 
    y = value,
    fill = reorder(country, value) == "GBR"
  ) +
  geom_col() +
  scale_fill_manual(values = c('steelblue', 'red'), guide = "none") +
  theme(
    axis.text.x = element_text(size = 6, angle = 45, vjust = 1.15, hjust = 1) 
  ) +
  ggtitle(
    "Cross country GDP per hour worked (Year 2020)",
    subtitle =  "indicator is measured in USD (constant prices 2010 and PPPs)"
  ) +
  labs(
    x = "Country", 
    y = "GDP per hour worked ($)\n"
  ) 
  
```

View cross country GDP per hour worked for 2020 (2015 index)
```{r}
gdp_phw %>% 
  mutate(year = year(year)) %>% 
  filter(
    measure == "IDX2015",
    year == 2020
    ) %>%  
  select(-c(indicator, frequency, measure, subject, year, flag_codes)) %>%  
  ggplot() +
  aes(
    x = reorder(country, value), 
    y = value,
    fill = reorder(country, value) == "GBR"
    ) +
  geom_col() +
  scale_fill_manual(values = c('steelblue', 'red'), guide = "none") +
  theme(
    axis.text.x = element_text(size = 6, angle = 45, vjust = 1.15, hjust = 1)
    ) +
  ggtitle(
    "GDP per hour worked (Year 2020)",
    subtitle =  "indicator is measured in USD (index 2015 = 100)"
  ) +
  labs(
    x = "Country", 
    y = "GDP per hour worked ($)\n"
  ) 
```

<br>
__View Investment by asset data__

View UK investment by Asset (% GFCF) time-series
```{r}
inv_asset %>%
  select(-c(indicator, frequency, flag_codes)) %>%
  filter(country == "GBR") %>%
  ggplot() +
  aes(x = year, y = value, colour = subject) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("UK investment by Asset") +
  labs(
    x = "\n Year", 
    y = "Investment (% of GFCF) \n",
    colour = "Asset type"
  ) 
```

OTHMACHINEQT: Information and Communication Technology (ICT) equipment (computer software and databases, telecommunications equipment and computer hardware)

CULTASSET: cultivated biological resources (managed forests, livestock raised for milk production, etc.)

OTHBUILDING: other buildings and structures (roads, bridges, airfields, dams, etc.)

FIXASSET: intellectual property products (such as R&D, mineral exploration, software and databases, and literary and artistic originals, etc.)

TRANSPEQT: transport equipment (ships, trains, aircraft, etc.)

DWELLING: dwellings (excluding land)


View G-7 cross-country investment time-series
```{r}
gfcf %>%
  filter(
    country %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")
    ) %>%
  ggplot() +
  aes(x = year, y = gfcf_mln_usd, color = country) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "G-7 Cross country Investment (aka Gross Fixed Capital Formation)",
    subtitle =  "(current prices and current PPPs)"
  ) +
  labs(
    x = "\n Year", 
    y = "GFCF ($MM) \n",
    colour = "Country"
  ) 
```


Join investment by asset with GFCF data
```{r}
inv_asset_usd <- inv_asset %>% 
  arrange(country, subject, year) %>% 
  left_join(gfcf, by = c("country", "year")) %>% 
  mutate(
    value_mln_usd = value * gfcf_mln_usd / 100
  )

```


View UK investment by asset time-series
```{r}
inv_asset_usd %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(country == "GBR") %>%
  ggplot() +
  aes(x = year, y = value_mln_usd, colour = subject) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("UK investment by asset") +
  labs(
    x = "\n Year", 
    y = "Investment ($MM) \n",
    colour = "Asset type"
  ) 

```




<br>
__OECD Education Spending Expenditure__

View UK education expenditure (% of GDP) by type time-series
```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(country == "GBR") %>%
  ggplot() +
  aes(x = year, y = value, colour = subject) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("UK public spending on education") +
  labs(
    x = "\n Year", 
    y = "Expenditure (% of GDP) \n",
    colour = "Education type"
  ) 

```

TRY : TeRtiarY
PRY_NTRY: PRimarY to post-secondary Non-TeRtiarY
PRY_TRY: PRimarY to TeRtiarY


View G-7 cross-country GDP time-series
```{r}
gdp %>%
  filter(
    country %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")
  ) %>%
  ggplot() +
  aes(x = year, y = gdp_mln_usd, color = country) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "G-7 Cross country GDP",
    subtitle =  "(current PPPs)"
  ) +
  labs(
    x = "\n Year",
    y = "GDP ($MM) \n",
    colour = "Country"
  ) 
```
Join education expenditure with GDP data
```{r}
edu_exp_usd <- edu_exp %>% 
  left_join(gdp, by = c("country", "year")) %>% 
  mutate(
    value_mil_usd = value * gdp_mln_usd / 100
  )

```


View UK expenditure on education time-series
```{r}
edu_exp_usd %>%
  filter(country == "GBR") %>%
  ggplot() +
  aes(x = year, y = value_mil_usd, colour = subject) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("UK public spending on education") +
  labs(
    x = "\n Year", 
    y = "Expenditure ($MM) \n",
    colour = "Education type"
  ) 

```



<br>
__Comparison of productivity by industry in UK and EU Countries__

View productivity by industry for Europe's large economies
```{r}
productivity_phw %>% 
  filter(
    Country %in% c("United Kingdom", "France", "Germany")
  ) %>% 
  ggplot() +
  aes(
    x = `A*10 (excl L)`, 
    y = Output_per_hour,
    fill = Country
    ) +
  geom_col(position = "dodge") +
  scale_fill_brewer(palette = "Dark2") +
  ggtitle(
    "Productivity by industry",
    subtitle =  "(Years: 2014 - 2016)"
  ) +
  labs(
    x = "\n NACE Industry", 
    y = "Output per hour (€)"
  ) 
```


```{r}
productivity_phw %>% 
  distinct(`A*10 (excl L)`, `NACE Industry`)
```













