---
title: "K-means Clustering"
author: "John Hios"
date: "15/06/2022"
output: html_notebook
---


<br>
__Library calls__
```{r}
library(here)
```


<br>
__Read cleaned data__
```{r}
source(here("scripts/clean_gdp_phw_data.R"))
source(here("scripts/clean_inv_asset_data.R"))
source(here("scripts/clean_gfcf_data.R"))
source(here("scripts/clean_edu_exp_data.R"))
source(here("scripts/clean_gdp_data.R"))
source(here("scripts/clean_hrs_wrkd_data.R"))
```

<br>
__OECD data: Labour Productivity__

Select the GDP per hour worked data (USD) of European countries
```{r}
gdp_phw_europe <- gdp_phw %>% 
  filter(
    country %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", 
                   "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", 
                   "LUX", "NLD", "NOR", "POL", "PRT", "ROU", "SVK", "SVN", 
                   "ESP", "SWE", "CHE", "GBR"),
    measure == "USD"
  ) %>% 
  select(-c(indicator, frequency, measure, subject, flag_codes)) %>% 
  rename(gdp_phw_usd = value) 
  
```


<br>
__OECD Data: Investment by Asset__

Select the Investment by Asset data (% GFCF) of European countries
```{r}
inv_asset_europe <- inv_asset %>%
  filter(
    country %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", 
                   "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", 
                   "LUX", "NLD", "NOR", "POL", "PRT", "ROU", "SVK", "SVN", 
                   "ESP", "SWE", "CHE", "GBR")
  ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    ict_pc_gfcf = OTHMACHINEQT,
    cultasset_pc_gfcf = CULTASSET,
    infrastuct_pc_gfcf = OTHBUILDING,
    intelprop_pc_gfcf = FIXASSET,
    transpeqt_pc_gfcf = TRANSPEQT,
    dwelling_pc_gfcf = DWELLING
  ) %>% 
  arrange(country, year)
```


<br>
__OECD Data: Investment (Gross Fixed Capital Formation)__

Select the GFCF data (mln USD) of European countries
```{r}
gfcf_europe <- gfcf %>% 
  filter(
    country %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", 
                   "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", 
                   "LUX", "NLD", "NOR", "POL", "PRT", "ROU", "SVK", "SVN", 
                   "ESP", "SWE", "CHE", "GBR")
  )
```


<br>
__OECD Data: Education Spending Expenditure__

Select the Expenditure on education data (% GDP) of European countries
```{r}
edu_exp_europe <- edu_exp %>%
  filter(
    country %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", 
                   "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", 
                   "LUX", "NLD", "NOR", "POL", "PRT", "ROU", "SVK", "SVN", 
                   "ESP", "SWE", "CHE", "GBR")
    ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    try_pc_gdp = TRY,
    pry_ntry_pc_gdp = PRY_NTRY,
    pry_try_pc_gdp = PRY_TRY
  ) %>%
  arrange(country, year)
```


<br>
__OECD Data: Gross Domestic Product (GDP)__

Select the GDP data (mln USD) of European countries
```{r}
gdp_europe <- gdp %>%
  filter(
    country %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", 
                   "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", 
                   "LUX", "NLD", "NOR", "POL", "PRT", "ROU", "SVK", "SVN", 
                   "ESP", "SWE", "CHE", "GBR")
  ) 
```


<br>
__OECD Data: Hrs worked__

Select the Hours Worked data (hrs) of European countries
```{r}
hrs_wrkd_europe <- hrs_wrkd %>%
  filter(
    country %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", 
                   "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", 
                   "LUX", "NLD", "NOR", "POL", "PRT", "ROU", "SVK", "SVN", 
                   "ESP", "SWE", "CHE", "GBR")
  )
```

#################################################################################################################################
#################################################################################################################################
#################################################################################################################################

<br>
__Data for clustering__

Left join of European country productivity and investment related data
```{r}
productivity_data <- gdp_phw_europe %>% 
  left_join(edu_exp_europe, by = c("country", "year")) %>% 
  left_join(inv_asset_europe, by = c("country", "year")) %>% 
  left_join(gdp_europe, by = c("country", "year")) %>% 
  left_join(gfcf_europe, by = c("country", "year")) %>% 
  left_join(hrs_wrkd_europe, by = c("country", "year"))

glimpse(productivity_data)
```

View data for clustering - year 2018 is selected because there are no more recent data available for the UK
```{r}
productivity_data %>% 
  mutate(year = year(year)) %>% 
  filter(year == 2018)
```

Drop European countries that don't have data for year 2018
```{r}
productivity_data %>% 
  mutate(year = year(year)) %>% 
  filter(year == 2018) %>% 
  drop_na()
```
The loss of data is not significant - only 8 countries out of 28 were removed from the dataset, therefore the analysis can proceed


To obtain a common basis of comparison for the above countries, we normalise all education expenditure and investment data in `USD per hour worked` 

This is a sensible choice since:

+ Productivity is measured in GDP (in USD) per hour worked

+ Education expenditure is measured as % of GDP

+ Investment by asset is measured as % of GFCF, which in turn is measured as % of GDP or in USD


```{r}
productivity_data <- productivity_data %>%
  mutate(year = year(year)) %>%
  filter(year == 2018) %>%
  drop_na() %>%
  mutate(
    try_phw_usd = try_pc_gdp * gdp_phw_usd / 100,
    pry_ntry_phw_usd = pry_ntry_pc_gdp * gdp_phw_usd / 100,
    pry_try_phw_usd = pry_try_pc_gdp * gdp_phw_usd / 100,
    ict_phw_usd = ict_pc_gfcf * gfcf_mln_usd / hr_wkd / 100,
    dwelling_phw_usd = dwelling_pc_gfcf * gfcf_mln_usd / hr_wkd / 100,
    infrastuct_phw_usd = infrastuct_pc_gfcf * gfcf_mln_usd / hr_wkd / 100,
    cultasset_phw_usd = cultasset_pc_gfcf * gfcf_mln_usd / hr_wkd / 100,
    transpeqt_phw_usd = transpeqt_pc_gfcf * gfcf_mln_usd / hr_wkd / 100,
    intelprop_phw_usd = intelprop_pc_gfcf * gfcf_mln_usd / hr_wkd / 100
  ) %>%
  select(
    country,
    year,
    gdp_phw_usd,
    try_phw_usd,
    pry_ntry_phw_usd,
    pry_try_phw_usd,
    ict_phw_usd,
    dwelling_phw_usd,
    infrastuct_phw_usd,
    cultasset_phw_usd,
    transpeqt_phw_usd,
    intelprop_phw_usd
)
```





<br>
__K-means clustering__

Prepare data for K-means clustering
```{r}
productivity_data <- productivity_data %>% 
  select(-year) %>% 
  column_to_rownames("country")
```

Standardise data
```{r}
productivity_data_scale <- productivity_data %>% 
  mutate(across(where(is.numeric), scale))

productivity_data_scale
```

Check data if mean == 0 and std == 1
```{r}
productivity_data_scale %>%
  pivot_longer(cols = everything(),
               names_to = "type", 
               values_to = "value") %>% #convert data to long format
  group_by(type) %>%
  summarise(mean = round(mean(value)), 
            sd = sd(value))
```


<br>
__Manual selection of clusters__

Initial guess of 4 clusters (k=4) to group countries

This is based on productivity data and the share of Europe's  Nominal GDP [https://www.wikiwand.com/en/Financial_and_social_rankings_of_sovereign_states_in_Europe]
```{r}
set.seed(340717) # to reproduce results shown in presentation

clust_data_scale <- kmeans(productivity_data_scale, 
                        centers = 4, 
                        nstart = 25)

clust_data_scale
```

```{r}
library(broom)

tidy(clust_data_scale, 
     col.names = colnames(productivity_data_scale))
```

```{r}
augment(clust_data_scale, productivity_data)
```


Clustering Metrics
```{r}
glance(clust_data_scale)
```

<br>
__Algorithmic selection of clusters__

```{r}
# Set min & max number of clusters want to look at 
max_k <- 15 

k_clusters <- tibble(k = 1:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(productivity_data_scale, .x, nstart = 25)), 
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, productivity_data)
  )

k_clusters
```

```{r}
clusterings <- k_clusters %>% 
  unnest(c(glanced))

clusterings
```


Choosing the number of clusters

`Method # 1: Elbow method`

```{r}
ggplot(clusterings, aes(x = k, y = tot.withinss)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = seq(1,20, by = 1))
```

If you want to use a function to do the plot above, use this:
```{r}
library(factoextra)

fviz_nbclust(productivity_data_scale,
             kmeans,
             method = "wss",
             nstart = 25)
```


`Method # 2: Silhouette coefficient`
```{r}
fviz_nbclust(productivity_data_scale, kmeans, method = "silhouette", nstart = 25)
```


`Method # 3: Gap statistic`
```{r}
fviz_nbclust(productivity_data_scale, kmeans, method = "gap_stat", nstart = 100) 
```

<br>
`Method #2` indicates k=4 clusters and `Method #3` indicates k=9 clusters. For 20 data points, k=4 is a sensible choice.  

Check of education expenditure and key investment assets vs productivity for k=4:

```{r}
clusterings %>% 
  unnest(cols = c(augmented)) %>% 
  filter(k == 4) %>% 
  ggplot(
    aes(x = gdp_phw_usd, y = try_phw_usd, colour = .cluster, label = .rownames)
  ) +
  geom_point(aes(color = .cluster), size = 2.5) +
  geom_text(hjust = 0, vjust = - 0.75, size = 3) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "Relationship between Productivity and Education expenditure",
    subtitle = "(Year 2018)"
  ) +
  labs(
    x = "GDP per hours worked ($)", 
    y = "Tertiary education expenditure per hours worked ($) \n",
    colour = "Cluster"
  ) 
```

```{r}
clusterings %>% 
  unnest(cols = c(augmented)) %>% 
  filter(k == 4) %>% 
  ggplot(
    aes(x = gdp_phw_usd, y = intelprop_phw_usd, colour = .cluster, label = .rownames)
  ) +
  geom_point(aes(color = .cluster), size = 2.5) +
  geom_text(hjust = 0, vjust = - 0.75, size = 3) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "Relationship between Productivity and Intellectual property products",
    subtitle = "(Year 2018)"
  ) +
  labs(
    x = "GDP per hours worked ($)", 
    y = "Intellectual property investment per hours worked ($) \n",
    colour = "Cluster"
  ) 
```


```{r}
productivity_data %>% 
  names()
```


Average scores for each investment factor/asset split by cluster:
```{r}
clusterings %>% 
  unnest(augmented) %>% 
  filter(k == 4) %>% 
  group_by(.cluster) %>%
  summarise(mean(gdp_phw_usd), mean(try_phw_usd), mean(pry_ntry_phw_usd), 
            mean(pry_try_phw_usd), mean(ict_phw_usd), mean(dwelling_phw_usd),
            mean(infrastuct_phw_usd), mean(cultasset_phw_usd), 
            mean(transpeqt_phw_usd), mean(intelprop_phw_usd))
```


__Compare how the UK does (cluster 3) against France and Germany (cluster 4)__

Get row that corresponds to cluster 4
```{r}
cluster_4_fradeu <- clusterings %>% 
  unnest(augmented) %>% 
  filter(k == 4) %>% 
  group_by(.cluster) %>%
  summarise(mean(gdp_phw_usd), mean(try_phw_usd), mean(pry_ntry_phw_usd), 
            mean(pry_try_phw_usd), mean(ict_phw_usd), mean(dwelling_phw_usd),
            mean(infrastuct_phw_usd), mean(cultasset_phw_usd), 
            mean(transpeqt_phw_usd), mean(intelprop_phw_usd)) %>% 
  filter(.cluster %in% c(4)) 
  
cluster_4_fradeu
```

Calculate percentage difference of UK from the center of cluster 4
```{r}
100*(cluster_4_fradeu[1,2:11]-productivity_data["GBR", 1:10])/cluster_4_fradeu[1,2:11] 
```




















