---
title: "R Notebook"
output: html_notebook
---


<br>
__Library calls__
```{r}
library(here)
```


<br>
__Read cleaned data__
```{r}
source(here("scripts/clean_gdp_phw_data.R"))
source(here("scripts/clean_inv_asset_data.R"))
source(here("scripts/clean_gfcf_data.R"))
source(here("scripts/clean_edu_exp_data.R"))
source(here("scripts/clean_gdp_data.R"))
source(here("scripts/clean_hrs_wrkd_data.R"))
```


__Labour_Productivity-OECD_Countries__

GDP per hour worked data (European countries)
```{r}
gdp_phw_europe <- gdp_phw %>% 
  filter(
    country %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", 
                   "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", 
                   "LUX", "NLD", "NOR", "POL", "PRT", "ROU", "SVK", "SVN", 
                   "ESP", "SWE", "CHE", "GBR"),
    measure == "USD"
  ) %>% 
  select(-c(indicator, frequency, measure, subject, flag_codes)) %>% 
  rename(gdp_phw_usd = value) 
  
```


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################

__OECD Investment by Asset__


Investment by Asset (% GFCF) for European countries
```{r}
inv_asset_europe <- inv_asset %>%
  filter(
    country %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", 
                   "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", 
                   "LUX", "NLD", "NOR", "POL", "PRT", "ROU", "SVK", "SVN", 
                   "ESP", "SWE", "CHE", "GBR")
  ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    ict_pc_gfcf = OTHMACHINEQT,
    cultasset_pc_gfcf = CULTASSET,
    infrastuct_pc_gfcf = OTHBUILDING,
    intelprop_pc_gfcf = FIXASSET,
    transpeqt_pc_gfcf = TRANSPEQT,
    dwelling_pc_gfcf = DWELLING
  ) %>% 
  arrange(country, year)
```




##################################################################################################################################


OECD Investment GFCF

GFCF data (mln USD)
```{r}
gfcf_europe <- gfcf %>% 
  filter(
    country %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", 
                   "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", 
                   "LUX", "NLD", "NOR", "POL", "PRT", "ROU", "SVK", "SVN", 
                   "ESP", "SWE", "CHE", "GBR")
  )
```



#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__ECD Education Spending Expenditure__

Expenditure on education (% GDP)
```{r}
edu_exp_europe <- edu_exp %>%
  filter(
    country %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", 
                   "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", 
                   "LUX", "NLD", "NOR", "POL", "PRT", "ROU", "SVK", "SVN", 
                   "ESP", "SWE", "CHE", "GBR")
    ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    try_pc_gdp = TRY,
    pry_ntry_pc_gdp = PRY_NTRY,
    pry_try_pc_gdp = PRY_TRY
  ) %>%
  arrange(country, year)
```


#################################################################################################################################

__GDP-derived expenditure in USD__

OECD_Gross_Domestic_Product_GDP

GDP data (mln USD)
```{r}
gdp_europe <- gdp %>%
  filter(
    country %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", 
                   "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", 
                   "LUX", "NLD", "NOR", "POL", "PRT", "ROU", "SVK", "SVN", 
                   "ESP", "SWE", "CHE", "GBR")
  ) 
```

#################################################################################################################################
#################################################################################################################################
#################################################################################################################################

__OECD Hrs worked__

Hours Worked (hrs)
```{r}
hrs_wrkd_europe <- hrs_wrkd %>%
  filter(
    country %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", 
                   "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", 
                   "LUX", "NLD", "NOR", "POL", "PRT", "ROU", "SVK", "SVN", 
                   "ESP", "SWE", "CHE", "GBR")
  )
```

#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__OECD data for clustering__


```{r}
productivity_data <- gdp_phw_europe %>% 
  left_join(edu_exp_europe, by = c("country", "year")) %>% 
  left_join(inv_asset_europe, by = c("country", "year")) %>% 
  left_join(gdp_europe, by = c("country", "year")) %>% 
  left_join(gfcf_europe, by = c("country", "year")) %>% 
  left_join(hrs_wrkd_europe, by = c("country", "year"))

glimpse(productivity_data)
```


```{r}
productivity_data %>% 
  mutate(year = year(year)) %>% 
  filter(year == 2018)
```
Drop european countries that don't have data for 2018
```{r}
productivity_data %>% 
  mutate(year = year(year)) %>% 
  filter(year == 2018) %>% 
  drop_na()
```
The loss of data is not significant



```{r}
productivity_data <- productivity_data %>% 
  mutate(year = year(year)) %>% 
  filter(year == 2018) %>% 
  drop_na() %>% 
  mutate(
    try_phw_usd = try_pc_gdp * gdp_phw_usd / 100,
    pry_ntry_phw_usd = pry_ntry_pc_gdp * gdp_phw_usd / 100,
    pry_try_phw_usd = pry_try_pc_gdp * gdp_phw_usd / 100,
    ict_phw_usd = ict_pc_gfcf * gfcf_mln_usd / hr_wkd / 100,
    dwelling_phw_usd = dwelling_pc_gfcf * gfcf_mln_usd / hr_wkd / 100,
    infrastuct_phw_usd = infrastuct_pc_gfcf * gfcf_mln_usd / hr_wkd / 100,
    cultasset_phw_usd = cultasset_pc_gfcf * gfcf_mln_usd / hr_wkd / 100,
    transpeqt_phw_usd = transpeqt_pc_gfcf * gfcf_mln_usd / hr_wkd / 100,
    intelprop_phw_usd = intelprop_pc_gfcf * gfcf_mln_usd / hr_wkd / 100
  ) %>% 
  select(
    country,
    year,
    gdp_phw_usd,
    try_phw_usd, 
    pry_ntry_phw_usd, 
    pry_try_phw_usd, 
    ict_phw_usd, 
    dwelling_phw_usd, 
    infrastuct_phw_usd, 
    cultasset_phw_usd,
    transpeqt_phw_usd,
    intelprop_phw_usd
  )
```
#################################################################################################################################


Prepare data for K-means clustering
```{r}
productivity_data <- productivity_data %>% 
  select(-year) %>% 
  column_to_rownames("country")
```

Standardise data
```{r}
productivity_data_scale <- productivity_data %>% 
  mutate(across(where(is.numeric), scale))

productivity_data_scale
```

Check data if mean == 0 and std == 1
```{r}
productivity_data_scale %>%
  pivot_longer(cols = everything(),
               names_to = "type", 
               values_to = "value") %>% #convert data to long format
  group_by(type) %>%
  summarise(mean = round(mean(value)), 
            sd = sd(value))
```


Clustering with K-means
```{r}
set.seed(340717)

clust_data_scale <- kmeans(productivity_data_scale, 
                        centers = 4, 
                        nstart = 25)

clust_data_scale
```

```{r}
library(broom)

tidy(clust_data_scale, 
     col.names = colnames(productivity_data_scale))
```

```{r}
augment(clust_data_scale, productivity_data)
```


Clustering Metrics

```{r}
glance(clust_data_scale)
```


```{r}
library(broom)

# Set min & max number of clusters want to look at 
max_k <- 15 

k_clusters <- tibble(k = 1:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(productivity_data_scale, .x, nstart = 25)), 
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, productivity_data)
  )

k_clusters
```

```{r}
clusterings <- k_clusters %>% 
  unnest(c(glanced))

clusterings
```


Choosing the number of clusters

__Elbow method__

```{r}
ggplot(clusterings, aes(x = k, y = tot.withinss)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = seq(1,20, by = 1))
```

If you want to use a function to do the plot above, use this:
```{r}
library(factoextra)

fviz_nbclust(productivity_data_scale,
             kmeans,
             method = "wss",
             nstart = 25)
```


__Silhouette coefficient__
```{r}
fviz_nbclust(productivity_data_scale, kmeans, method = "silhouette", nstart = 25)
```


__Gap statistic__
```{r}
fviz_nbclust(productivity_data_scale, kmeans, method = "gap_stat", nstart = 100) 
```


Method #2 indicates k=4 clusters and method #3 indicates k=9 clusters. For 20 data points, k=4 is a sensible choice.  

Let's see if k=4 is sufficient

```{r}
clusterings %>% 
  unnest(cols = c(augmented)) %>% 
  filter(k == 4) %>% 
  ggplot(aes(x = gdp_phw_usd, y = try_phw_usd, colour = .cluster, label = .rownames)) +
  geom_point(aes(color = .cluster), size = 2.5) +
  geom_text(hjust = 0, vjust = - 0.75, size = 3) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "Relationship between Productivity and Education expenditure",
    subtitle = "(Year 2018)"
  ) +
  labs(
    x = "GDP per hours worked ($)", 
    y = "Tertiary education expenditure per hours worked ($) \n",
    colour = "Cluster"
  ) 
```

```{r}
clusterings %>% 
  unnest(cols = c(augmented)) %>% 
  filter(k == 4) %>% 
  ggplot(aes(x = gdp_phw_usd, y = intelprop_phw_usd, colour = .cluster, label = .rownames)) +
  geom_point(aes(color = .cluster), size = 2.5) +
  geom_text(hjust = 0, vjust = - 0.75, size = 3) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "Relationship between Productivity and Intellectual property products",
    subtitle = "(Year 2018)"
  ) +
  labs(
    x = "GDP per hours worked ($)", 
    y = "Intellectual property investment per hours worked ($) \n",
    colour = "Cluster"
  ) 
```


```{r}
productivity_data %>% 
  names()
```


What are the average scores for each investment factor/asset split by cluster?
```{r}
clusterings %>% 
  unnest(augmented) %>% 
  filter(k == 4) %>% 
  group_by(.cluster) %>%
  summarise(mean(gdp_phw_usd), mean(try_phw_usd), mean(pry_ntry_phw_usd), 
            mean(pry_try_phw_usd), mean(ict_phw_usd), mean(dwelling_phw_usd),
            mean(infrastuct_phw_usd), mean(cultasset_phw_usd), mean(transpeqt_phw_usd),
            mean(intelprop_phw_usd))
```


__Compare how the UK does (cluster 3) against France and Germany in cluster 4__

Get row that corresponds to cluster 4
```{r}
cluster_4_fradeu <- clusterings %>% 
  unnest(augmented) %>% 
  filter(k == 4) %>% 
  group_by(.cluster) %>%
  summarise(mean(gdp_phw_usd), mean(try_phw_usd), mean(pry_ntry_phw_usd), 
            mean(pry_try_phw_usd), mean(ict_phw_usd), mean(dwelling_phw_usd),
            mean(infrastuct_phw_usd), mean(cultasset_phw_usd), mean(transpeqt_phw_usd),
            mean(intelprop_phw_usd)) %>% 
  filter(.cluster %in% c(4)) 
  
cluster_4_fradeu
```

Calculate percentage difference of UK from the center of cluster 4
```{r}
100*(cluster_4_fradeu[1,2:11]-productivity_data["GBR", 1:10])/cluster_4_fradeu[1,2:11] 
```




















