---
title: "R Notebook"
output: html_notebook
---


<br>
__Library calls__
```{r}
library(here)
```

<br>
__Read cleaned data__
```{r}
source(here("scripts/clean_gdp_phw_data.R"))
source(here("scripts/clean_inv_asset_data.R"))
source(here("scripts/clean_gfcf_data.R"))
source(here("scripts/clean_edu_exp_data.R"))
source(here("scripts/clean_gdp_data.R"))
```


<br>
__OECD data: Labour Productivity__

Select the G-7 cross-country GDP per hour worked data
```{r}
gdp_phw_g7 <- gdp_phw %>% 
  filter(
    country %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "USD"
  ) %>% 
  select(-c(indicator, frequency, measure, subject, flag_codes)) %>% 
  rename(gdp_phw_usd = value) 
  
```


<br>
__OECD data: Public Spending on Education and GDP__

Select the G-7 cross-country expenditure on education (million USD)
```{r}
edu_exp_g7 <- edu_exp %>%
  filter(
    country %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
  ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    try_pc_gdp = TRY,
    pry_ntry_pc_gdp = PRY_NTRY,
    pry_try_pc_gdp = PRY_TRY
  ) %>% 
  left_join(gdp, by = c("country", "year"))%>% 
  mutate(
    try_mln_usd = try_pc_gdp * gdp_mln_usd / 100,
    pry_ntry_mln_usd = pry_ntry_pc_gdp * gdp_mln_usd / 100,
    pry_try_mln_usd = pry_try_pc_gdp * gdp_mln_usd / 100
  ) %>% 
  select(-try_pc_gdp, -pry_ntry_pc_gdp, -pry_try_pc_gdp, -gdp_mln_usd) %>% 
  arrange(country, year)
```



<br>
__OECD Data: Investment by Asset and GFCF__

Select the G-7 cross-country investment by asset (million USD)
```{r}
inv_asset_g7 <- inv_asset %>%
  filter(
    country %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")
    ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    ict = OTHMACHINEQT,
    cultasset = CULTASSET,
    infrastuct = OTHBUILDING,
    intelprop = FIXASSET,
    transpeqt = TRANSPEQT,
    dwelling = DWELLING
  ) %>% 
  left_join(gfcf, by = c("country", "year")) %>% 
  mutate(
    ict_mln_usd = ict * gfcf_mln_usd / 100,
    cultasset_mln_usd = cultasset * gfcf_mln_usd / 100,
    infrastuct_mln_usd = infrastuct * gfcf_mln_usd / 100,
    intelprop_mln_usd = intelprop * gfcf_mln_usd / 100,
    transpeqt_mln_usd = transpeqt * gfcf_mln_usd / 100,
    dwelling_mln_usd = dwelling * gfcf_mln_usd / 100
  ) %>% 
  select(-gfcf_mln_usd, -ict, -cultasset, -infrastuct, -intelprop, -transpeqt, -dwelling) %>% 
  arrange(country, year)
```



<br>
__Data for modelling__

Prepare data for linear regression model
```{r}
productivity <- gdp_phw_g7 %>% 
  left_join(edu_exp_g7, by = c("country", "year")) %>% 
  left_join(inv_asset_g7, by = c("country", "year")) 

glimpse(productivity)
```

Trim UK data
```{r}
prod_uk_trim <- productivity %>% 
  mutate(year = year(year)) %>%
  filter(
    country == "GBR",
    year >= 1995 & year <=2019
  ) %>% 
  select(
    gdp_phw_usd, 
    ict_mln_usd,
    cultasset_mln_usd,
    infrastuct_mln_usd,
    intelprop_mln_usd,
    transpeqt_mln_usd,
    dwelling_mln_usd
  ) %>% 
  mutate(
    ict_bln_usd = ict_mln_usd / 1000,
    cultasset_bln_usd = cultasset_mln_usd / 1000,
    infrastuct_bln_usd = infrastuct_mln_usd / 1000,
    intelprop_bln_usd = intelprop_mln_usd / 1000,
    transpeqt_bln_usd = transpeqt_mln_usd / 1000,
    dwelling_bln_usd = dwelling_mln_usd / 1000
  ) %>% 
  select(
    -ict_mln_usd,
    -cultasset_mln_usd,
    -infrastuct_mln_usd,
    -intelprop_mln_usd,
    -transpeqt_mln_usd,
    -dwelling_mln_usd
  )
```



Check for aliases
```{r}
alias(lm(gdp_phw_usd ~ ., data = prod_uk_trim))
```


Call libraries for linear regression modelling 
```{r}
library(GGally)
library(ggfortify)
library(modelr)
```


Check data for correlations between variables
```{r}
ggpairs(prod_uk_trim)
```


<br>
__Automated modelling__

Consider models with up to 6 predictors and pairwise interactions
```{r}
library(glmulti)
glmulti_fit <- glmulti(
  gdp_phw_usd ~ ., 
  data = prod_uk_trim,
  level = 2, # 2 = include pairwise interactions, 1 = main effects only (main effect = no pairwise interactions)
  minsize = 0, # no min size of model
  maxsize = 6, # -1 = no max size of model
  marginality = TRUE, # marginality here means the same as 'strongly hierarchical' interactions, i.e. include pairwise interactions only if both predictors present in the model as main effects.
  method = "g", # the problem is too large for exhaustive search, so search using a genetic algorithm
  crit = bic, # criteria for model selection is BIC value (lower is better)
  plotty = FALSE, # don't plot models as function runs
  report = TRUE, # do produce reports as function runs
  confsetsize = 100, # return best 100 solutions
  fitfunction = lm # fit using the `lm` function
)
```
Summary of `glmulti` run results
```{r}
summary(glmulti_fit)
```

```{r}
# here is the best model (lowest BIC) from the glmulti run above
glmulti_fit@objects[1]


# if you want to see the other models
weightable(glmulti_fit)
```

<br>
__Best model summary (6 regressor terms - predictors and pairwise interactions)__
```{r}
# View summary of the best model (lowest BIC) from the glmulti run above
mod_auto1 <- lm(gdp_phw_usd ~ 1 + cultasset_bln_usd + infrastuct_bln_usd +
                 intelprop_bln_usd + dwelling_bln_usd + 
                 infrastuct_bln_usd:cultasset_bln_usd + 
                 dwelling_bln_usd:infrastuct_bln_usd,
                   data = prod_uk_trim)

summary(mod_auto1)
```

```{r}
# let's see diagnostic plots
autoplot(mod_auto1)
```
The diagnostic plots don't look that great, and the `cultasset_bln_usd` coefficient is not statistically significant

Let's check what the other models calculated by the gmulti algorithm are like


<br>
__Summary of model with 4 regressor terms (5th best model from `gmulti` run)__
```{r}
# View summary of model 
mod_auto5 <- lm(gdp_phw_usd ~ 1 + infrastuct_bln_usd + intelprop_bln_usd +
                dwelling_bln_usd + dwelling_bln_usd:infrastuct_bln_usd,
                   data = prod_uk_trim)

summary(mod_auto5)
```

```{r}
# let's see diagnostic plots
autoplot(mod_auto5)
```


<br>
__Summary of model with 6 regressor terms (8th best model from `gmulti` run)__
```{r}
# View summary of model 
mod_auto8 <- lm(gdp_phw_usd ~ 1 + ict_bln_usd + cultasset_bln_usd +
                  infrastuct_bln_usd + dwelling_bln_usd + 
                  cultasset_bln_usd:ict_bln_usd + dwelling_bln_usd:infrastuct_bln_usd,
                   data = prod_uk_trim)

summary(mod_auto8)
```

```{r}
# let's see diagnostic plots
autoplot(mod_auto8)
```

<br>
__Interpretation of diagnostic plots__

The diagnostic plots don't look that great, although all predictor coefficients are statistically significant

The model with the 4 regressor terms (`mod_auto5`) is a good trade-off between accuracy and model parsimony



<br>
__Model with 4 regressor terms (5th best model from `gmulti` run)__

View portion of variance explained by each model parameter
```{r}
library(relaimpo)

calc.relimp(mod_auto5, type = "lmg", rela = TRUE)
```

<br>
__K-fold cross validation__

Create folds for model cross-validation
```{r}
library(caret)
set.seed(765977) # to reproduce results shown in presentation
# set up options for train function below
cv_10_fold <- trainControl(method = "cv", # cross-validation
                           number = 10, # 10-fold
                           savePredictions = TRUE) # save all predictions
```

Cross validation of model with 4 regressor terms (5th best model from `gmulti` run - `mod_auto5`)
```{r}
model_4regr_kfold <- train(gdp_phw_usd ~ 1 + infrastuct_bln_usd +
                               intelprop_bln_usd + dwelling_bln_usd + 
                               dwelling_bln_usd:infrastuct_bln_usd,
                             data = prod_uk_trim,
                             trControl = cv_10_fold, # use options defined above
                             method = 'lm')
```


```{r}
model_4regr_kfold$resample
```

Summary of K-fold runs
```{r}
tibble(
  model = "Linear model with 4 regressor terms",
  mean_RMSE = mean(model_4regr_kfold$resample$RMSE),
  mean_Rsquared = mean(model_4regr_kfold$resample$Rsquared)
)
```


















