---
title: "R Notebook"
output: html_notebook
---


Call Libraries
```{r}
library(janitor)
library(fastDummies)
library(tidyverse)
library(here)
library(readxl)
```



__Compare productivity by industry in UK and EU Countries__


Load Data
```{r}
prod_industry_phw <- read_excel(here("raw_data/International_Labour_Productivity-Europe.xls"), sheet = "Table 1 R-proc")
prod_industry_growth <- read_excel(here("raw_data/International_Labour_Productivity-Europe.xls"), sheet = "Table 2 R-proc")


glimpse(prod_industry_phw)
glimpse(prod_industry_growth)
```



Check for NA values
```{r}
prod_industry_phw %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
prod_industry_growth %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```



#################################################################################################################################


Transpose tibbles and clean names
```{r}
prod_industry_phw_data <- prod_industry_phw %>%
  mutate(`A*10 (excl L)` = str_c("sector_", `A*10 (excl L)`)) %>% 
  select(-`NACE Industry`) %>% 
  pivot_longer(-`A*10 (excl L)`, names_to = "Country", values_to = "Output_per_hour") %>% 
  pivot_wider(names_from = "A*10 (excl L)", values_from = "Output_per_hour") %>% 
  arrange(Country) %>% 
  clean_names()
  

prod_industry_growth_data <- prod_industry_growth %>%
  mutate(`A*10 (excl L)` = str_c("sector_", `A*10 (excl L)`)) %>% 
  select(-`NACE Industry`) %>% 
  pivot_longer(-`A*10 (excl L)`, names_to = "Country", values_to = "Labour_Productivity_Growth") %>%  
  pivot_wider(names_from = "A*10 (excl L)", values_from = "Labour_Productivity_Growth") %>% 
  arrange(Country)%>% 
  clean_names()


prod_industry_phw_data
prod_industry_growth_data
```

#################################################################################################################################

Read data
```{r}
gdp_phw <- read_csv(here("raw_data/OECD_GDP_per_Hour_Worked_JHios.csv")) %>% 
  clean_names()

glimpse(gdp_phw)
```
```{r}
gdp_phw_27 <- gdp_phw%>% 
  filter(
    location %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", "FRA",
                 "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "NLD",
                 "NOR", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE", "CHE",
                 "GBR"),
    time == 2016,
    measure == "USD"
  ) %>% 
  select(location, value) %>% 
  arrange(location) %>% 
  rename(gdp_phw_usd = value) %>% 
  mutate(country = c("Austria", "Belgium", "Bulgaria", "Switzerland", "Czech Republic",
                     "Germany", "Denmark", "Spain", "Estonia", "Finland", 
                     "France", "United Kingdom", "Greece", "Croatia", "Hungary",
                     "Ireland", "Italy", "Lithuania", "Luxembourg", "Latvia", 
                     "Netherlands", "Norway", "Poland", "Portugal", "Romania", 
                     "Slovakia", "Slovenia",  "Sweden"
                      )) %>% 
  select(-location)

```

Add GDP phw data
```{r}
prod_industry_phw_data <- prod_industry_phw_data  %>% 
  left_join(gdp_phw_27, by = "country" ) %>% 
  filter(country != "Cyprus")


```




#################################################################################################################################



Prepare data for K-means clustering
```{r}
prod_industry_phw_data <- prod_industry_phw_data %>% 
  column_to_rownames("country")

prod_industry_phw_data
```

Standardise data
```{r}
prod_industry_data_scale <- prod_industry_phw_data %>% 
  mutate(across(where(is.numeric), scale))

prod_industry_data_scale
```

Check data if mean==0 and std==1
```{r}
prod_industry_data_scale %>%
  pivot_longer(cols = everything(),
               names_to = "type", 
               values_to = "value") %>% #convert data to long format
  group_by(type) %>%
  summarise(mean = round(mean(value)), 
            sd = sd(value))
```


Clustering with K-means

```{r}
# set.seed(1234)

clust_industry_data_scale <- kmeans(prod_industry_data_scale, 
                        centers = 4, 
                        nstart = 25)

clust_industry_data_scale
```

```{r}
library(broom)

tidy(clust_industry_data_scale, 
     col.names = colnames(prod_industry_data_scale))
```



```{r}
augment(clust_industry_data_scale, prod_industry_phw_data)
```


Clustering Metrics

```{r}
glance(clust_industry_data_scale)
```


```{r}
library(broom)

# Set min & max number of clusters want to look at 
max_k <- 15 

k_clusters <- tibble(k = 1:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(prod_industry_data_scale, .x, nstart = 25)), 
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, prod_industry_phw_data)
  )

k_clusters
```

```{r}
clusterings <- k_clusters %>% 
  unnest(c(glanced))

clusterings
```

Choosing the number of clusters

__Elbow method__

```{r}
ggplot(clusterings, aes(x = k, y = tot.withinss)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = seq(1,20, by = 1))
```

If you want to use a function to do the plot above, use this:
```{r}
library(factoextra)

fviz_nbclust(prod_industry_data_scale,
             kmeans,
             method = "wss",
             nstart = 25)
```


__Silhouette coefficient__
```{r}
fviz_nbclust(prod_industry_data_scale, kmeans, method = "silhouette", nstart = 25)
```


__Gap statistic__
```{r}
fviz_nbclust(prod_industry_data_scale, kmeans, method = "gap_stat", nstart = 100) #would put nstart=25 if had more computing power
```




Methods #2 and #3 indicate k=2 clusters is sufficient

```{r}
clusterings %>% 
  unnest(cols = c(augmented)) %>% 
  filter(k == 2) %>% 
  ggplot(aes(x = gdp_phw_usd, y = sector_a, colour = .cluster, label = .rownames)) +
  geom_point(aes(color = .cluster)) +
  geom_text(hjust = 0, vjust = - 0.5, size = 3) +
  scale_colour_brewer(palette = "Dark2") 
```


```{r}
clusterings %>% 
  unnest(cols = c(augmented)) %>% 
  filter(k == 2) %>% 
  ggplot(aes(x = sector_j, y = sector_k, colour = .cluster, label = .rownames)) +
  geom_point(aes(color = .cluster)) +
  geom_text(hjust = 0, vjust = - 0.5, size = 3) +
  scale_colour_brewer(palette = "Dark2") 
```

#################################################################################################################################

```{r}
prod_industry_phw %>% 
  select(`A*10 (excl L)`, `NACE Industry`)
```


```{r}
clusterings %>% 
  group_by(augmented) %>%
  summarise(mean(gdp_phw_usd), mean(sector_a), mean(sector_b_e), 
            mean(sector_f), mean(sector_g_i), mean(sector_j),
            mean(sector_k), mean(sector_m_n), mean(sector_o_q),
            mean(sector_r_u))
```






