---
title: "R Notebook"
output: html_notebook
---


Call Libraries
```{r}
library(tidyverse)
library(janitor)
library(here)
```


__Labour_Productivity-OECD_Countries__

Read data
```{r}
gdp_phw <- read_csv(here("raw_data/OECD_GDP_per_Hour_Worked_JHios.csv")) 

glimpse(gdp_phw)
```

Check for NA values
```{r}
gdp_phw %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```



```{r}
gdp_phw %>% 
  select(-c(INDICATOR, FREQUENCY, SUBJECT, `Flag Codes`)) %>% 
  filter(
    # LOCATION %in% c("G-7", "EU28", "CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # LOCATION %in% c("G-7", "EU28", "GBR"),
    MEASURE == "USD") %>% 
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "GDP per hour worked",
    subtitle =  "indicator is measured in USD (constant prices 2010 and PPPs)"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP per hour worked ($) \n"
  ) 
  
```



#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Cross Country Gross Domestic Spending on R&D__

Read data
```{r}
gdexp_rnd <- read_csv(here("raw_data/OECD_Gross_Domestic_Spending_on_R&D_JHios.csv")) 

glimpse(gdexp_rnd)
```

G-7 countries gross domestic expenditure on R&D (Million USD)
```{r}
gdexp_rnd %>%
  select(-c(INDICATOR, FREQUENCY, SUBJECT, `Flag Codes`)) %>%
  filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
         MEASURE == "MLN_USD") %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 countries gross domestic expenditure on R&D") +
  labs(
    x = "\n Year", 
    y = "Expenditure ($MM) \n"
  ) 
```
################################################################ KEEP THIS FIGURE!!!!
G-7 countries gross domestic expenditure on R&D (% GDP)
```{r}
gdexp_rnd %>%
  select(-c(INDICATOR, FREQUENCY, SUBJECT, `Flag Codes`)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # LOCATION %in% c( "FRA", "DEU", "USA", "GBR"),
    MEASURE == "PC_GDP"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 countries gross domestic expenditure on R&D") +
  labs(
    x = "\n Year", 
    y = "Expenditure (% of GDP) \n"
  ) 
```


##################################################################################################################
##################################################################################################################

__Check with GDP-derived expenditure in USD__

OECD_Gross_Domestic_Product_GDP

Read data
```{r}
gdp <- read_csv(here("raw_data/OECD_Gross_Domestic_Product_GDP_JHios.csv")) 

glimpse(gdp)
```

Check for NA's
```{r}
gdp %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
gdp %>% 
  # distinct(LOCATION)
  distinct(INDICATOR) # GDP
  # distinct(SUBJECT) # TOT
  # distinct(MEASURE) # MLN_USD, USD_CAP
  # distinct(FREQUENCY) #A
  # distinct(`Flag Codes`) # NA, E, P, B, D
```




```{r}
gdp %>%
  select(-c(INDICATOR, FREQUENCY, SUBJECT, `Flag Codes`)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    MEASURE == "MLN_USD"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, group = LOCATION, color = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country GDP") +
  labs(
    x = "\n Year",
    y = "GDP ($MM) \n"
  ) +
  scale_x_continuous(breaks = seq(from = 1960, to = 2020, by = 10))
```


```{r}
gdexp_rnd_test <- gdexp_rnd %>%
  select(-c(INDICATOR, FREQUENCY, SUBJECT, `Flag Codes`)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    MEASURE == "PC_GDP"
  ) 
```

```{r}
gdp_light <- gdp %>%
  filter(MEASURE == "MLN_USD") %>%
  select(LOCATION, TIME, Value) %>%
  rename(gdp_mln_usd = Value)


gdexp_rnd_test <- gdexp_rnd %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    MEASURE == "PC_GDP"
  ) %>%
  select(-c(INDICATOR, FREQUENCY, SUBJECT, MEASURE, `Flag Codes`)) %>%
  rename(gdexp_rnd_pc_gdp = Value) %>% 
  left_join(gdp_light, by = c("LOCATION", "TIME")) %>%
  mutate(
    Value_mln_usd = gdexp_rnd_pc_gdp * gdp_mln_usd / 100
  ) %>%
  select(LOCATION, TIME, Value_mln_usd)

gdexp_rnd_test
```


G-7 Cross country R&D ($MM)
```{r}
gdexp_rnd_test %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")) %>%
  ggplot() +
  aes(x = TIME, y = Value_mln_usd, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "G-7 Cross country R&D Test!!!"
  ) +
  labs(
    x = "\n Year", 
    y = "R&D ($MM) \n"
  ) 
```


```{r}

gdexp_rnd_uk <- gdexp_rnd  %>%
  select(-c(INDICATOR, FREQUENCY, SUBJECT, `Flag Codes`)) %>%
  filter(
    LOCATION %in% c("GBR"),
    # LOCATION %in% c( "FRA", "DEU", "USA", "GBR"),
    MEASURE == "PC_GDP"
    ) 


gdexp_rnd_testuk <- gdexp_rnd_test  %>%
  filter(
    LOCATION %in% c("GBR")
    ) 


ggplot() +
  aes(x = gdexp_rnd_testuk$Value_mln_usd, y = gdexp_rnd_uk$Value) +
   geom_point() +
  # scale_colour_gradient()
  # scale_colour_gradient(low = "gray0", high = "gray100")
  # geom_point(color = "steelblue") +
  # geom_text(
  #   aes(label = TIME),
  #   nudge_x = 1.5,
  #   nudge_y = 0,
  #   size = 2.5
  # ) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0)
```



#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Compare investment between UK and other countries__


Cross country infrastructure investment

Read data
```{r}
infr_inv <- read_csv(here("raw_data/OECD_Infrastructure_Investment_JHios.csv")) 

glimpse(infr_inv)
```


Check for NA's
```{r}
infr_inv %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
infr_inv %>% 
  distinct(SUBJECT, MEASURE)
```



G-7 Cross country infrastructure investment (Euros)
```{r}
infr_inv %>%
  select(-c(INDICATOR, FREQUENCY, `Flag Codes`)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # SUBJECT == "RAIL",
    SUBJECT == "ROAD",
    # SUBJECT == "SEA",
    # SUBJECT == "AIR",
    MEASURE == "EUR") %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country infrastructure investment") +
  labs(
    x = "\n Year", 
    y = "Investment (€) \n"
  ) 
```


G-7 Cross country infrastructure investment (% of GDP)
```{r}
infr_inv %>%
  select(-c(INDICATOR, FREQUENCY, `Flag Codes`)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    SUBJECT == "INLAND",
    MEASURE == "PC_GDP") %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "G-7 Cross country infrastructure investment",
    subtitle = "(Type: Inland)"
  ) +
  labs(
    x = "\n Year", 
    y = "Investment (% of GDP) \n"
  ) 
```

##########################################################################################

OECD_Gross_Domestic_Product_GDP

Read data
```{r}
gdp <- read_csv(here("raw_data/OECD_Gross_Domestic_Product_GDP_JHios.csv")) 

glimpse(gdp)
```

Check for NA's
```{r}
gdp %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
gdp %>% 
  # distinct(LOCATION)
  distinct(INDICATOR) # GDP
  # distinct(SUBJECT) # TOT
  # distinct(MEASURE) # MLN_USD, USD_CAP
  # distinct(FREQUENCY) #A
  # distinct(`Flag Codes`) # NA, E, P, B, D
```




```{r}
gdp %>%
  select(-c(INDICATOR, FREQUENCY, SUBJECT, `Flag Codes`)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    MEASURE == "MLN_USD"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, group = LOCATION, color = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country GDP") +
  labs(
    x = "\n Year",
    y = "GDP ($MM) \n"
  ) +
  scale_x_continuous(breaks = seq(from = 1960, to = 2020, by = 10))
```


```{r}
gdp_light <- gdp %>%
  filter(MEASURE == "MLN_USD") %>%
  select(LOCATION, TIME, Value) %>%
  rename(gdp = Value)


inv_inland_usd <- infr_inv %>%
  select(-c(INDICATOR, FREQUENCY, SUBJECT, `Flag Codes`)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    SUBJECT == "INLAND",
    MEASURE == "PC_GDP"
  ) %>%
  left_join(gdp_light, by = c("LOCATION", "TIME")) %>%
  mutate(
    value_mmusd = Value * gdp / 100
  )

inv_inland_usd
```


G-7 Cross country INLAND infrastructure investment ($MM)
```{r}
inv_inland_usd %>%
  select(-c(SUBJECT, MEASURE, Value, gdp)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")) %>%
  ggplot() +
  aes(x = TIME, y = value_mmusd, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "G-7 Cross country infrastructure investment",
    subtitle = "(Type: Inland)"
  ) +
  labs(
    x = "\n Year", 
    y = "Investment ($MM) \n"
  ) 
```



#################################################################################################################################
#################################################################################################################################


OECD Investment by Asset

Read data
```{r}
inv_asset <- read_csv(here("raw_data/OECD_Investment_by_Asset_JHios.csv")) 

glimpse(inv_asset)
```


Check for NA's
```{r}
inv_asset %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```



```{r}
inv_asset %>% 
  # distinct(LOCATION)
  # distinct(INDICATOR) # GFCFASSET
  distinct(SUBJECT) # OTHMACHINEQT, CULTASSET, OTHBUILDING, FIXASSET, TRANSPEQT, DWELLING
  # distinct(MEASURE) # PC_GFCF
  # distinct(FREQUENCY) #A
  # distinct(`Flag Codes`) # NA, E, B
```


OTHMACHINEQT: Information and Communication Technology (ICT) equipment (computer software and databases, telecommunications equipment and computer hardware)

CULTASSET: cultivated biological resources (managed forests, livestock raised for milk production, etc.)

OTHBUILDING: other buildings and structures (roads, bridges, airfields, dams, etc.)

FIXASSET: intellectual property products (such as R&D, mineral exploration, software and databases, and literary and artistic originals, etc.)

TRANSPEQT: transport equipment (ships, trains, aircraft, etc.)

DWELLING: dwellings (excluding land)


G-7 Cross country investment by Asset (% GFCF)
```{r}
inv_asset %>%
  select(-c(INDICATOR, FREQUENCY, `Flag Codes`)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # SUBJECT == "OTHMACHINEQT",
    # SUBJECT == "CULTASSET",
    # SUBJECT == "OTHBUILDING",
    SUBJECT == "FIXASSET",
    # SUBJECT == "TRANSPEQT",
    # SUBJECT == "DWELLING"
  ) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country investment by Asset") +
  labs(
    x = "\n Year", 
    y = "Investment (% GFCF) \n"
  ) 
```

OECD Investment GFCF


Read data
```{r}
gfcf <- read_csv(here("raw_data/OECD_Investment_GFCF_JHios.csv")) 

glimpse(gfcf)
```

```{r}
gfcf <- gfcf %>%
  mutate(TIME = as.numeric(TIME))
```



Check for NA's
```{r}
gfcf %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
gfcf %>% 
  # distinct(LOCATION)
  # distinct(INDICATOR) # GFCF
  # distinct(SUBJECT) # TOT
  distinct(MEASURE) # AGRWTH, MLN_USD, QGRWTH
  # distinct(FREQUENCY) #A, Q
  # distinct(`Flag Codes`) # NA, E, P, B, D
```

AGRWTH: Annual growth (%)
MLN_USD: Million US Dollars
QGRWTH: Quarterly growth rate (%)

```{r}
gfcf %>%
  select(-c(INDICATOR, FREQUENCY, SUBJECT, `Flag Codes`)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    MEASURE == "MLN_USD"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, group = LOCATION, color = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country investment by Asset") +
  labs(
    x = "\n Year", 
    y = "GFCF ($MM) \n"
  ) +
  scale_x_continuous(breaks = seq(from = 1960, to = 2020, by = 10))
```


```{r}
gfcf_light <- gfcf %>% 
  filter(MEASURE == "MLN_USD") %>% 
  select(LOCATION, TIME, Value) %>% 
  rename(gfcf = Value)

inv_asset_usd <- inv_asset %>% 
  left_join(gfcf_light, by = c("LOCATION", "TIME")) %>% 
  mutate(
    value_mmusd = Value * gfcf / 100
  )

```


G-7 Cross country investment by Asset (million USD)
```{r}
inv_asset_usd %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, MEASURE, Value, gfcf)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # SUBJECT == "OTHMACHINEQT",
    # SUBJECT == "CULTASSET",
    # SUBJECT == "OTHBUILDING",
    # SUBJECT == "FIXASSET",
    # SUBJECT == "TRANSPEQT",
    SUBJECT == "DWELLING"
  ) %>%
  ggplot() +
  aes(x = TIME, y = value_mmusd, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country investment by Asset") +
  labs(
    x = "\n Year", 
    y = "Investment ($MM) \n"
  ) 
```
OTHMACHINEQT: Information and Communication Technology (ICT) equipment (computer software and databases, telecommunications equipment and computer hardware)

CULTASSET: cultivated biological resources (managed forests, livestock raised for milk production, etc.)

OTHBUILDING: other buildings and structures (roads, bridges, airfields, dams, etc.)

FIXASSET: intellectual property products (such as R&D, mineral exploration, software and databases, and literary and artistic originals, etc.)

TRANSPEQT: transport equipment (ships, trains, aircraft, etc.)

DWELLING: dwellings (excluding land)


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


OECD Education Spending Expenditure


Read data
```{r}
edu_exp <- read_csv(here("raw_data/OECD_Public_Spending_on_Education_JHios.csv")) 

glimpse(edu_exp)
```



Check for NA's
```{r}
edu_exp %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


G-7 countries education expenditure (GDP percentage)
TRY : TeRtiarY
PRY_NTRY: PRimarY to post-secondary Non-TeRtiarY
PRY_TRY: PRimarY to TeRtiarY
```{r}
edu_exp %>%
  select(-c(INDICATOR, FREQUENCY, MEASURE, `Flag Codes`)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    SUBJECT == "TRY"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 
```


```{r}
edu_exp %>%
  select(-c(INDICATOR, FREQUENCY, MEASURE, `Flag Codes`)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    SUBJECT == "PRY_TRY"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Primary to tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```


```{r}
edu_exp %>%
  select(-c(INDICATOR, FREQUENCY, MEASURE, `Flag Codes`)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    SUBJECT == "PRY_NTRY"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Primary to post-secondary non-tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```


```{r}
edu_exp %>%
  select(-c(INDICATOR, FREQUENCY, MEASURE, `Flag Codes`)) %>%
  filter(LOCATION %in% c("GBR")) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = SUBJECT) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle("UK education expenditure") +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```

```{r}
# gdp_light <- gdp %>%
#   filter(MEASURE == "MLN_USD") %>%
#   select(LOCATION, TIME, Value) %>%
#   rename(gdp = Value)

edu_exp_usd <- edu_exp %>% 
  left_join(gdp_light, by = c("LOCATION", "TIME")) %>% 
  mutate(
    value_mmusd = Value * gdp / 100
  )

```


```{r}
edu_exp_usd %>%
  select(-c(INDICATOR, FREQUENCY, MEASURE, `Flag Codes`)) %>%
  filter(LOCATION %in% c("GBR")) %>%
  ggplot() +
  aes(x = TIME, y = value_mmusd, colour = SUBJECT) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle("UK education expenditure") +
  labs(
    x = "\n Year", 
    y = "GDP ($MM) \n"
  ) 

```

#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Modelling Dataset (REVIEW ONCE AGAIN)__


```{r}
gdp_phw %>% 
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    MEASURE == "USD"
  ) %>% 
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, SUBJECT, MEASURE)) %>% 
  rename(gdp_phw_usd = Value)
```


```{r}
gdexp_rnd %>%
  filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
         MEASURE == "MLN_USD") %>% 
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, SUBJECT, MEASURE)) %>%
  rename(gdexp_rnd_mmusd = Value)
```

```{r}
infr_inv %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")
  ) %>% 
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, MEASURE)) %>%
  pivot_wider(names_from = SUBJECT, values_from = Value) %>% 
  mutate(
    RAIL = RAIL/1e6,
    ROAD = ROAD/1e6,
    INLAND = INLAND,
    AIR = AIR/1e6,
    SEA = SEA/1e6,
    INLANDWATER = INLANDWATER/1e6
  ) %>%
  rename(
    rail_mmeuro = RAIL,
    road_mmeuro = ROAD,
    inland_pc_gdp = INLAND,
    air_mmeuro = AIR,
    sea_mmeuro = SEA,
    inlandwater_mmeuro = INLANDWATER
  )

```


```{r}
infr_inv %>% 
  distinct(SUBJECT, MEASURE)
```


```{r}
edu_exp_usd %>%
  filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")) %>% 
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, MEASURE))
```



















