---
title: "R Notebook"
output: html_notebook
---


Call Libraries
```{r}
library(tidyverse)
library(janitor)
library(here)
```


__Labour_Productivity-OECD_Countries__

Read data
```{r}
gdp_phw <- read_csv(here("raw_data/OECD_GDP_per_Hour_Worked_JHios.csv")) 

glimpse(gdp_phw)
```

Check for NA values
```{r}
gdp_phw %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```



```{r}
gdp_phw %>% 
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, SUBJECT)) %>% 
  filter(
    # LOCATION %in% c("G-7", "EU28", "CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # LOCATION %in% c("G-7", "EU28", "GBR"),
    MEASURE == "USD") %>% 
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "GDP per hour worked",
    subtitle =  "indicator is measured in USD (constant prices 2010 and PPPs)"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP per hour worked ($) \n"
  ) 
  
```



#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Cross Country Gross Domestic Spending on R&D__

Read data
```{r}
gdexp_rnd <- read_csv(here("raw_data/OECD_Gross_Domestic_Spending_on_R&D_JHios.csv")) 

glimpse(gdexp_rnd)
```

G-7 countries gross domestic expenditure on R&D (Million USD)
```{r}
gdexp_rnd %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, SUBJECT)) %>%
  filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
         MEASURE == "MLN_USD") %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 countries gross domestic expenditure on R&D") +
  labs(
    x = "\n Year", 
    y = "Expenditure ($MM) \n"
  ) 
```
################################################################ KEEP THIS FIGURE!!!!
G-7 countries gross domestic expenditure on R&D (% GDP)
```{r}
gdexp_rnd %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, SUBJECT)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # LOCATION %in% c( "FRA", "DEU", "USA", "GBR"),
    MEASURE == "PC_GDP"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 countries gross domestic expenditure on R&D") +
  labs(
    x = "\n Year", 
    y = "Expenditure (% of GDP) \n"
  ) 
```


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Compare investment between UK and other countries__


Cross country infrastructure investment

Read data
```{r}
infr_inv <- read_csv(here("raw_data/OECD_Infrastructure_Investment_JHios.csv")) 

glimpse(infr_inv)
```


Check for NA's
```{r}
infr_inv %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


G-7 Cross country infrastructure investment (Euros)
```{r}
infr_inv %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # SUBJECT == "RAIL",
    # SUBJECT == "ROAD",
    # SUBJECT == "SEA",
    SUBJECT == "AIR",
    # SUBJECT == "ROAD",
    MEASURE == "EUR") %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country infrastructure investment") +
  labs(
    x = "\n Year", 
    y = "Investment (€) \n"
  ) 
```


G-7 Cross country infrastructure investment (% of GDP)
```{r}
infr_inv %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    SUBJECT == "INLAND",
    MEASURE == "PC_GDP") %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "G-7 Cross country infrastructure investment",
    subtitle = "(Type: Inland)"
  ) +
  labs(
    x = "\n Year", 
    y = "Investment (% of GDP) \n"
  ) 
```

#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


OECD Education Spending Expenditure


Read data
```{r}
edu_exp <- read_csv(here("raw_data/OECD_Public_Spending_on_Education_JHios.csv")) 

glimpse(edu_exp)
```



Check for NA's
```{r}
edu_exp %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


G-7 countries education expenditure (GDP percentage)
TRY : TeRtiarY
PRY_NTRY: PRimarY to post-secondary Non-TeRtiarY
PRY_TRY: PRimarY to TeRtiarY
```{r}
edu_exp %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, MEASURE)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    SUBJECT == "TRY"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 
```


```{r}
edu_exp %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, MEASURE)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    SUBJECT == "PRY_TRY"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Primary to tTertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```


```{r}
edu_exp %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, MEASURE)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    SUBJECT == "PRY_NTRY"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Primary to post-secondary non-tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```


```{r}
edu_exp %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, MEASURE)) %>%
  filter(LOCATION %in% c("GBR")) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = SUBJECT) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle("UK education expenditure") +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```
















