---
title: "R Notebook"
output: html_notebook
---


Call Libraries
```{r}
library(tidyverse)
library(janitor)
library(here)
```


__Labour_Productivity-OECD_Countries__

Read data
```{r}
gdp_phw <- read_csv(here("raw_data/OECD_GDP_per_Hour_Worked_JHios.csv")) %>% 
  clean_names()

glimpse(gdp_phw)
```

Check for NA values
```{r}
gdp_phw %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```

```{r}
gdp_phw %>% 
  distinct(location)
  # distinct(INDICATOR) # GFCFASSET
  # distinct(subject) # OTHMACHINEQT, CULTASSET, OTHBUILDING, FIXASSET, TRANSPEQT, DWELLING
  # distinct(MEASURE) # PC_GFCF
  # distinct(FREQUENCY) #A
  # distinct(`Flag Codes`) # NA, E, B
```


View data
```{r}
gdp_phw %>% 
  select(-c(indicator, subject, frequency, flag_codes)) %>% 
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "USD") %>% 
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "GDP per hour worked",
    subtitle =  "indicator is measured in USD (constant prices 2010 and PPPs)"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP per hour worked ($) \n"
  ) 
  
```

G-7 GDP per hour worked data
```{r}
gdp_phw_g7 <- gdp_phw %>% 
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "USD"
  ) %>% 
  select(-c(indicator, frequency, measure, subject, flag_codes)) %>% 
  rename(gdp_phw_usd = value) 
  
```


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################

OECD Investment by Asset

Read data
```{r}
inv_asset <- read_csv(here("raw_data/OECD_Investment_by_Asset_JHios.csv")) %>% 
  clean_names()

glimpse(inv_asset)
```


Check for NA's
```{r}
inv_asset %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```



```{r}
inv_asset %>% 
  distinct(location)
  # distinct(INDICATOR) # GFCFASSET
  # distinct(subject) # OTHMACHINEQT, CULTASSET, OTHBUILDING, FIXASSET, TRANSPEQT, DWELLING
  # distinct(MEASURE) # PC_GFCF
  # distinct(FREQUENCY) #A
  # distinct(`Flag Codes`) # NA, E, B
```


OTHMACHINEQT: Information and Communication Technology (ICT) equipment (computer software and databases, telecommunications equipment and computer hardware)

CULTASSET: cultivated biological resources (managed forests, livestock raised for milk production, etc.)

OTHBUILDING: other buildings and structures (roads, bridges, airfields, dams, etc.)

FIXASSET: intellectual property products (such as R&D, mineral exploration, software and databases, and literary and artistic originals, etc.)

TRANSPEQT: transport equipment (ships, trains, aircraft, etc.)

DWELLING: dwellings (excluding land)


G-7 Cross country investment by Asset (% GFCF)
```{r}
inv_asset %>%
  select(-c(indicator, frequency, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # subject== "OTHMACHINEQT",
    # subject == "CULTASSET",
    # subject == "OTHBUILDING",
    subject == "FIXASSET",
    # subject == "TRANSPEQT",
    # subject == "DWELLING"
  ) %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country investment by Asset") +
  labs(
    x = "\n Year", 
    y = "Investment (% GFCF) \n"
  ) 
```



G-7 investment by Asset (% GFCF)
```{r}
inv_asset_g7 <- inv_asset %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")
    ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    ict_pc_gfcf = OTHMACHINEQT,
    cultasset_pc_gfcf = CULTASSET,
    infrastuct_pc_gfcf = OTHBUILDING,
    intelprop_pc_gfcf = FIXASSET,
    transpeqt_pc_gfcf = TRANSPEQT,
    dwelling_pc_gfcf = DWELLING
  ) %>% 
  arrange(location, time)
```




##################################################################################################################################


OECD Investment GFCF


Read data
```{r}
gfcf <- read_csv(here("raw_data/OECD_Investment_GFCF_JHios.csv")) %>% 
  clean_names()

glimpse(gfcf)
```

```{r}
gfcf <- gfcf %>%
  mutate(time = as.numeric(time))
```


Check for NA's
```{r}
gfcf %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```
The timestamps missing relate to the Annual growth index (AGRWTH) - not affecting the scope of this analysis 

```{r}
gfcf %>% 
  distinct(location)
  # distinct(INDICATOR) # GFCF
  # distinct(SUBJECT) # TOT
  # distinct(measure) # AGRWTH, MLN_USD, QGRWTH
  # distinct(FREQUENCY) #A, Q
  # distinct(`Flag Codes`) # NA, E, P, B, D
```

AGRWTH: Annual growth (%)
MLN_USD: Million US Dollars
QGRWTH: Quarterly growth rate (%)

```{r}
gfcf %>%
  select(-c(indicator, frequency, subject, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "MLN_USD"
    ) %>%
  ggplot() +
  aes(x = time, y = value, color = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country investment by Asset") +
  labs(
    x = "\n Year", 
    y = "GFCF ($MM) \n"
  ) +
  scale_x_continuous(breaks = seq(from = 1960, to = 2020, by = 10))
```


GFCF data (mln USD)
```{r}
gfcf_g7 <- gfcf %>% 
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "MLN_USD"
  ) %>% 
  select(location, time, value) %>% 
  rename(gfcf_mln_usd = value)
```



#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


OECD Education Spending Expenditure


Read data
```{r}
edu_exp <- read_csv(here("raw_data/OECD_Public_Spending_on_Education_JHios.csv")) %>% 
  clean_names()

glimpse(edu_exp)
```



Check for NA's
```{r}
edu_exp %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```

```{r}
edu_exp %>% 
  distinct(location)
  # distinct(INDICATOR) # 
  # distinct(SUBJECT) # 
  # distinct(measure) # 
  # distinct(FREQUENCY) #
  # distinct(`Flag Codes`) #
```



UK education expenditure (% GDP)
TRY : TeRtiarY
PRY_NTRY: PRimarY to post-secondary Non-TeRtiarY
PRY_TRY: PRimarY to TeRtiarY

```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(location %in% c("GBR")) %>%
  ggplot() +
  aes(x = time, y = value, colour = subject) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle("UK education expenditure") +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```

G-7 expenditure on education (% GDP)
```{r}
edu_exp_g7 <- edu_exp %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")
    ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    try_pc_gdp = TRY,
    pry_ntry_pc_gdp = PRY_NTRY,
    pry_try_pc_gdp = PRY_TRY
  ) %>%
  arrange(location, time)
```


#################################################################################################################################

__GDP-derived expenditure in USD__

OECD_Gross_Domestic_Product_GDP

Read data
```{r}
gdp <- read_csv(here("raw_data/OECD_Gross_Domestic_Product_GDP_JHios.csv")) %>% 
  clean_names()

glimpse(gdp)
```

Check for NA's
```{r}
gdp %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
gdp %>% 
  distinct(location)
  # distinct(indicator) # GDP
  # distinct(SUBJECT) # TOT
  # distinct(MEASURE) # MLN_USD, USD_CAP
  # distinct(FREQUENCY) #A
  # distinct(`Flag Codes`) # NA, E, P, B, D
```

View data
```{r}
gdp %>%
  select(-c(indicator, subject, frequency, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "MLN_USD"
    ) %>%
  ggplot() +
  aes(x = time, y = value, group = location, color = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country GDP") +
  labs(
    x = "\n Year",
    y = "GDP ($MM) \n"
  ) +
  scale_x_continuous(breaks = seq(from = 1960, to = 2020, by = 10))
```



GDP data (mln USD)
```{r}
gdp_g7 <- gdp %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "MLN_USD"
  ) %>% 
  select(location, time, value) %>%
  rename(gdp_mln_usd = value)
```

#################################################################################################################################
#################################################################################################################################
#################################################################################################################################

__OECD Hrs worked__

OECD_Hours_Worked

Read data
```{r}
hrswrkd <- read_csv(here("raw_data/OECD_Hours_Worked_JHios.csv")) %>% 
  clean_names()

glimpse(hrswrkd)
```

Check for NA's
```{r}
hrswrkd %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
hrswrkd %>% 
  # distinct(location)
  # distinct(indicator) #
  # distinct(SUBJECT) # 
  # distinct(measure) # HR_WKD
  # distinct(FREQUENCY) #
  # distinct(`Flag Codes`) #
```

View data
```{r}
hrswrkd %>%
  select(-c(indicator, subject, frequency, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "HR_WKD"
    ) %>%
  ggplot() +
  aes(x = time, y = value, group = location, color = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country Hours Worked") +
  labs(
    x = "\n Year",
    y = "Hours Worked (hr) \n"
  ) +
  scale_x_continuous(breaks = seq(from = 1960, to = 2020, by = 10))
```



Hours Worked (hrs)
```{r}
hrswrkd_g7 <- hrswrkd %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "HR_WKD"
  ) %>% 
  select(location, time, value) %>%
  rename(hrs_wrkd = value)
```


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Data for clustering__


```{r}
productivity_data <- gdp_phw_g7 %>% 
  left_join(edu_exp_g7, by = c("location", "time")) %>% 
  left_join(inv_asset_g7, by = c("location", "time")) %>% 
  left_join(gdp_g7, by = c("location", "time")) %>% 
  left_join(gfcf_g7, by = c("location", "time")) %>% 
  left_join(hrswrkd_g7, by = c("location", "time"))

glimpse(productivity_data)
```


```{r}
productivity_data %>% 
  filter(time == 2018)
```

JPN	2018 : replace NA with median of other countries for 2018 ict_pc_gfcf
CAN	2018 : replace NA with median of other countries for 2018 cultasset_pc_gfcf
USA	2018 : replace NA with median of other countries for 2018 cultasset_pc_gfcf

```{r}
productivity_data <- productivity_data %>% 
  mutate(
    ict_pc_gfcf = coalesce(ict_pc_gfcf, median(ict_pc_gfcf, na.rm = TRUE)),
    cultasset_pc_gfcf = coalesce(cultasset_pc_gfcf, median(cultasset_pc_gfcf, na.rm = TRUE))
  )
```


```{r}
productivity_data <- productivity_data %>% 
  mutate(
    try_phw_usd = try_pc_gdp * gdp_phw_usd / 100,
    pry_ntry_phw_usd = pry_ntry_pc_gdp * gdp_phw_usd / 100,
    pry_try_phw_usd = pry_try_pc_gdp * gdp_phw_usd / 100,
    ict_phw_usd = ict_pc_gfcf * gfcf_mln_usd / hrs_wrkd / 100,
    dwelling_phw_usd = dwelling_pc_gfcf * gfcf_mln_usd / hrs_wrkd / 100,
    infrastuct_phw_usd = infrastuct_pc_gfcf * gfcf_mln_usd / hrs_wrkd / 100,
    cultasset_phw_usd = cultasset_pc_gfcf * gfcf_mln_usd / hrs_wrkd / 100,
    transpeqt_phw_usd = transpeqt_pc_gfcf * gfcf_mln_usd / hrs_wrkd / 100,
    intelprop_phw_usd = intelprop_pc_gfcf * gfcf_mln_usd / hrs_wrkd / 100
  ) %>% 
  select(
    location,
    time,
    gdp_phw_usd,
    try_phw_usd, 
    pry_ntry_phw_usd, 
    pry_try_phw_usd, 
    ict_phw_usd, 
    dwelling_phw_usd, 
    infrastuct_phw_usd, 
    cultasset_phw_usd,
    transpeqt_phw_usd,
    intelprop_phw_usd
  )
```


Prepare data for dendrogram
```{r}
productivity_data <- productivity_data %>% 
  filter(time == 2018) %>%
  select(-time) %>% 
  column_to_rownames("location")
```

Standardise data
```{r}
productivity_data_scale <- productivity_data %>% 
  mutate(across(where(is.numeric), scale))

productivity_data_scale
```
Check data if mean==0 and std==1
```{r}
productivity_data_scale %>%
  pivot_longer(cols = everything(),
               names_to = "type", 
               values_to = "value") %>% #convert data to long format
  group_by(type) %>%
  summarise(mean = round(mean(value)), 
            sd = sd(value))
```

Check if variables are correlated
```{r}
GGally::ggcorr(productivity_data_scale,
    label = TRUE,
    label_size = 3, 
    label_round = 2, 
    label_alpha = TRUE,
    hjust = 1,
    layout.exp = 0.5
  )
```



Call libraries
```{r}
library(cluster)
library(factoextra)
library(dendextend)
library(corrplot)
```


#################################################################################################################################

Take productivity GDP pwh
```{r}
diss_matrix_gdp_phw <- productivity_data_scale %>%
              select(gdp_phw_usd) %>%
              dist(method = "euclidean") 
```

Create a dissimilarity matrix showing distances
```{r}
fviz_dist(diss_matrix_gdp_phw)
```

Build dendrogram
```{r}
clusters_gdp_phw <- diss_matrix_gdp_phw %>%
                 hclust(method = "complete")
```

```{r}
clusters_gdp_phw %>%
  plot(cex = 0.5, hang = -5)
```


#################################################################################################################################

Take investments on TRY
```{r}
diss_matrix_try_phw_usd <- productivity_data_scale %>%
              select(try_phw_usd) %>%
              dist(method = "euclidean") 
```

Create a dissimilarity matrix showing distances
```{r}
fviz_dist(diss_matrix_try_phw_usd)
```
Bild dendrogram
```{r}
clusters_try_phw_usd <- diss_matrix_try_phw_usd %>%
                 hclust(method = "complete")
```

```{r}
clusters_try_phw_usd %>%
  plot(cex = 0.5, hang = -5)
```
#################################################################################################################################

Take pinestments on PRY_NTRY
```{r}
diss_matrix_pry_ntry_phw_usd <- productivity_data_scale %>%
              select(pry_ntry_phw_usd) %>%
              dist(method = "euclidean") 
```

Create a dissimilarity matrix showing distances
```{r}
fviz_dist(diss_matrix_pry_ntry_phw_usd)
```

Bild dendrogram
```{r}
clusters_pry_ntry_phw_usd <- diss_matrix_pry_ntry_phw_usd %>%
                 hclust(method = "complete")
```

```{r}
clusters_pry_ntry_phw_usd %>%
  plot(cex = 0.5, hang = -5)
```

#################################################################################################################################

Take investments on PRY_TRY
```{r}
diss_matrix_pry_try_phw_usd <- productivity_data_scale %>%
              select(pry_try_phw_usd) %>%
              dist(method = "euclidean") 
```

Create a dissimilarity matrix showing distances
```{r}
fviz_dist(diss_matrix_pry_try_phw_usd)
```

Bild dendrogram
```{r}
clusters_pry_try_phw_usd <- diss_matrix_pry_try_phw_usd %>%
                 hclust(method = "complete")
```

```{r}
clusters_pry_try_phw_usd %>%
  plot(cex = 0.5, hang = -5)
```

#################################################################################################################################

Take investments on ICT
```{r}
diss_matrix_ict_phw_usd <- productivity_data_scale %>%
              select(ict_phw_usd) %>%
              dist(method = "euclidean") 
```

Create a dissimilarity matrix showing distances
```{r}
fviz_dist(diss_matrix_ict_phw_usd)
```



Bild dendrogram
```{r}
clusters_ict_phw_usd <- diss_matrix_ict_phw_usd %>%
                 hclust(method = "complete")
```

```{r}
clusters_ict_phw_usd %>%
  plot(cex = 0.5, hang = -5)
```

#################################################################################################################################

Take investments on Dwelling
```{r}
diss_matrix_dwelling_phw_usd <- productivity_data_scale %>%
              select(dwelling_phw_usd) %>%
              dist(method = "euclidean") 
```

Create a dissimilarity matrix showing distances
```{r}
fviz_dist(diss_matrix_dwelling_phw_usd)
```
  
Bild dendrogram
```{r}
clusters_dwelling_phw_usd <- diss_matrix_dwelling_phw_usd %>%
                 hclust(method = "complete")
```

```{r}
clusters_dwelling_phw_usd %>%
  plot(cex = 0.5, hang = -5)
```

#################################################################################################################################

Take investments on Infrastructure
```{r}
diss_matrix_infrastuct_phw_usd <- productivity_data_scale %>%
              select(infrastuct_phw_usd) %>%
              dist(method = "euclidean") 
```

Create a dissimilarity matrix showing distances
```{r}
fviz_dist(diss_matrix_infrastuct_phw_usd)
```

Bild dendrogram
```{r}
clusters_infrastuct_phw_usd <- diss_matrix_infrastuct_phw_usd %>%
                 hclust(method = "complete")
```

```{r}
clusters_infrastuct_phw_usd %>%
  plot(cex = 0.5, hang = -5)
```


#################################################################################################################################

Take investments on Cultasset
```{r}
diss_matrix_cultasset_phw_usd <- productivity_data_scale %>%
              select(cultasset_phw_usd) %>%
              dist(method = "euclidean") 
```

Create a dissimilarity matrix showing distances
```{r}
fviz_dist(diss_matrix_cultasset_phw_usd)
```

Bild dendrogram
```{r}
clusters_cultasset_phw_usd <- diss_matrix_cultasset_phw_usd %>%
                 hclust(method = "complete")
```

```{r}
clusters_cultasset_phw_usd %>%
  plot(cex = 0.5, hang = -5)
```

#################################################################################################################################

Take investments on Transpeqt
```{r}
diss_matrix_transpeqt_phw_usd <- productivity_data_scale %>%
              select(transpeqt_phw_usd) %>%
              dist(method = "euclidean") 
```

Create a dissimilarity matrix showing distances
```{r}
fviz_dist(diss_matrix_transpeqt_phw_usd)
```  

Bild dendrogram
```{r}
clusters_transpeqt_phw_usd <- diss_matrix_transpeqt_phw_usd %>%
                 hclust(method = "complete")
```

```{r}
clusters_transpeqt_phw_usd %>%
  plot(cex = 0.5, hang = -5)
```


#################################################################################################################################

Take investments on intelprop
```{r}
diss_matrix_intelprop_phw_usd <- productivity_data_scale %>%
              select(intelprop_phw_usd) %>%
              dist(method = "euclidean") 
```

Create a dissimilarity matrix showing distances
```{r}
fviz_dist(diss_matrix_intelprop_phw_usd)
```  

Bild dendrogram
```{r}
clusters_intelprop_phw_usd <- diss_matrix_intelprop_phw_usd %>%
                 hclust(method = "complete")
```

```{r}
clusters_intelprop_phw_usd %>%
  plot(cex = 0.5, hang = -5)
```


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Compare productivity by industry in UK and EU Countries__

Load Data
```{r}
productivity_phw <- read_excel(here("raw_data/International_Labour_Productivity-Europe.xls"), sheet = "Table 1 R-proc")
productivity_growth <- read_excel(here("raw_data/International_Labour_Productivity-Europe.xls"), sheet = "Table 2 R-proc")


glimpse(productivity_phw)
glimpse(productivity_growth)
```



Check for NA values
```{r}
productivity_phw %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
productivity_growth %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```



Pivot data to long format
```{r}
tidy_productivity_phw <- productivity_phw %>%
  pivot_longer(-c(`A*10 (excl L)`, `NACE Industry`), names_to = "Country", values_to = "Output_per_hour") 

tidy_productivity_growth <- productivity_growth %>%
  pivot_longer(-c(`A*10 (excl L)`, `NACE Industry`), names_to = "Country", values_to = "Labour_Productivity_Growth") 


tidy_productivity_phw
tidy_productivity_growth
```

```{r}
tidy_productivity_phw %>% 
  filter(
    # `NACE Industry` == "Agriculture, forestry and fishing"
    # `NACE Industry` == "Industry (except construction)"
    # `NACE Industry` == "Construction"
    # `NACE Industry` == "Wholesale and retail trade, transport, accommodation and food service activities"
    `NACE Industry` == "Information and communication"
    # `NACE Industry` == "Financial and insurance activities"
    # `NACE Industry` == "Professional, scientific and technical activities; administrative and support service activities"
    # `NACE Industry` == "Public administration, defence, education, human health and social work activities"
    # `NACE Industry` == "Arts, entertainment and recreation; other service activities"
  ) %>% 
  ggplot() +
  aes(
    x = reorder(Country, Output_per_hour), 
    y = Output_per_hour,
    fill = reorder(Country, Output_per_hour) == "United Kingdom"
    ) +
  geom_col() +
  scale_fill_manual(values = c('steelblue', 'red'), guide = "none") +
  theme(
    axis.text.x = element_text(size = 6, angle = 45, vjust = 1, hjust = 1)
  ) +
  ggtitle(
    "Output per hour by industry .....",
    subtitle =  "(Years: 2014 - 2016)"
  ) +
  labs(
    x = "Country", 
    y = "Output per hour (€)"
  ) 
```


```{r}
tidy_productivity_growth %>% 
  filter(
    # `NACE Industry` == "Agriculture, forestry and fishing"
    # `NACE Industry` == "Industry (except construction)"
    # `NACE Industry` == "Construction"
    # `NACE Industry` == "Wholesale and retail trade, transport, accommodation and food service activities"
    `NACE Industry` == "Information and communication"
    # `NACE Industry` == "Financial and insurance activities"
    # `NACE Industry` == "Professional, scientific and technical activities; administrative and support service activities"
    # `NACE Industry` == "Public administration, defence, education, human health and social work activities"
    # `NACE Industry` == "Arts, entertainment and recreation; other service activities"
  ) %>%  
  ggplot() +
  aes(
    x = reorder(Country, Labour_Productivity_Growth), 
    y = Labour_Productivity_Growth,
    fill = reorder(Country, Labour_Productivity_Growth) == "United Kingdom"
    ) +
  geom_col() +
  scale_fill_manual(values = c('steelblue', 'red'), guide = "none") +
  theme(
    axis.text.x = element_text(size = 6,angle = 45, vjust = 1, hjust = 1)
    ) +
  ggtitle(
    "Labour Productivity Growth by industry ..... ",
    subtitle =  "(Years: 2014 - 2016)"
  ) +
  labs(
    x = "Country", 
    y = "Labour Productivity Growth (%)"
  ) 
```

Comparison with large economies in Europe: UK, France, Germany, Italy, Spain (the Netherlands)
```{r}
tidy_productivity_phw %>% 
  filter(
    Country %in% c("United Kingdom", "France", "Germany")
  ) %>% 
  ggplot() +
  aes(
    x = `A*10 (excl L)`, 
    y = Output_per_hour,
    fill = Country
    ) +
  geom_col(position = "dodge") +
  scale_fill_brewer(palette = "Dark2") +
  ggtitle(
    "Output per hour by industry",
    subtitle =  "(Years: 2014 - 2016)"
  ) +
  labs(
    x = "\n NACE Industry", 
    y = "Output per hour (€)"
  ) 
```
```{r}
tidy_productivity_phw %>% 
  distinct(`A*10 (excl L)`, `NACE Industry`)
```


```{r}
tidy_productivity_growth %>% 
  filter(
    Country %in% c("United Kingdom", "France", "Germany")
  ) %>% 
  ggplot() +
  aes(
    x = `A*10 (excl L)`, 
    y = Labour_Productivity_Growth,
    fill = Country
    ) +
  geom_col(position = "dodge") +
  scale_fill_brewer(palette = "Dark2") +
  ggtitle(
    "Labour Productivity Growth by industry",
    subtitle =  "(Years: 2014 - 2016)"
  ) +
  labs(
    x = "\n NACE Industry", 
    y = "Labour Productivity Growth (%)"
  ) 
```



Comparison with most productive countries in Europe (2017): UK, Ireland, Norway
```{r}
tidy_productivity_phw %>% 
  filter(
    Country %in% c("United Kingdom", "Ireland", "Norway")
  ) %>% 
  ggplot() +
  aes(
    x = `A*10 (excl L)`, 
    y = Output_per_hour,
    fill = Country
    ) +
  geom_col(position = "dodge") +
  scale_fill_brewer(palette = "Dark2") +
  ggtitle(
    "Output per hour by industry",
    subtitle =  "(Years: 2014 - 2016)"
  ) +
  labs(
    x = "\n NACE Industry", 
    y = "Output per hour (€)"
  ) 
```


Comparison with large economies in Europe: UK, France, Germany, Italy, Spain (the Netherlands)
Output per hour by industry 2014-16


```{r}
productivity_phw %>% 
  select(France, `United Kingdom`, Germany, Spain, Italy) %>% 
  summarise(
    sum_France = sum(France),
    sum_UK = sum(`United Kingdom`),
    sum_Germany = sum(Germany),
    sum_Spain = sum(Spain),
    sum_Italy = sum(Italy)
  )
  
```







