---
title: "R Notebook"
output: html_notebook
---


Call Libraries
```{r}
library(tidyverse)
library(janitor)
library(here)
library(readxl)
library(lubridate)
```


__Labour_Productivity-OECD_Countries__

Read data
```{r}
gdp_phw <- read_csv(here("raw_data/OECD_GDP_per_Hour_Worked_JHios.csv")) %>% 
  clean_names() 

glimpse(gdp_phw)
```

Change time in datetime format
```{r}
gdp_phw <- gdp_phw %>%
  mutate(time = make_datetime(time)) 
```

Check for NA values
```{r}
gdp_phw %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


View data
```{r}
gdp_phw %>% 
  select(-c(indicator, subject, frequency, flag_codes)) %>% 
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "USD") %>% 
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "GDP per hour worked",
    subtitle =  "indicator is measured in USD (constant prices 2010 and PPPs)"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP per hour worked ($) \n",
    colour = "Country"
  ) 
  
```

G-7 GDP per hour worked data
```{r}
gdp_phw_g7 <- gdp_phw %>% 
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "USD"
  ) %>% 
  select(-c(indicator, frequency, measure, subject, flag_codes)) %>% 
  rename(gdp_phw_usd = value) 
  
```


```{r}
gdp_phw %>% 
  mutate(time = year(time)) %>% 
  filter(
    # LOCATION %in% c("G-7", "EU28", "CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "USD",
    time == 2020
    ) %>%  
  select(-c(indicator, frequency, measure, subject, time, flag_codes)) %>%  
  ggplot() +
  aes(
    x = reorder(location, value), 
    y = value,
    fill = reorder(location, value) == "GBR"
    ) +
  geom_col() +
  scale_fill_manual(values = c('steelblue', 'red'), guide = "none") +
  theme(
    axis.text.x = element_text(size = 6, angle = 45, vjust = 1.15, hjust = 1) ) +
  ggtitle(
    "GDP per hour worked (Year 2020)",
    subtitle =  "indicator is measured in USD (constant prices 2010 and PPPs)"
  ) +
  labs(
    x = "Country", 
    y = "GDP per hour worked ($)\n"
  ) 
  
```


```{r}
gdp_phw %>% 
  mutate(time = year(time)) %>% 
  filter(
    # LOCATION %in% c("G-7", "EU28", "CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "IDX2015",
    time == 2020
    ) %>%  
  select(-c(indicator, frequency, measure, subject, time, flag_codes)) %>%  
  ggplot() +
  aes(
    x = reorder(location, value), 
    y = value,
    fill = reorder(location, value) == "GBR"
    ) +
  geom_col() +
  scale_fill_manual(values = c('steelblue', 'red'), guide = "none") +
  theme(
    axis.text.x = element_text(size = 6, angle = 45, vjust = 1.15, hjust = 1)
    ) +
  ggtitle(
    "GDP per hour worked (Year 2020)",
    subtitle =  "indicator is measured in USD (index 2015 = 100)"
  ) +
  labs(
    x = "Country", 
    y = "GDP per hour worked ($)\n"
  ) 
```



#################################################################################################################################
#################################################################################################################################
#################################################################################################################################

__OECD Investment by Asset__

Read data
```{r}
inv_asset <- read_csv(here("raw_data/OECD_Investment_by_Asset_JHios.csv")) %>% 
  clean_names()

glimpse(inv_asset)
```

Change time in datetime format
```{r}
inv_asset <- inv_asset %>%
  mutate(time = make_datetime(time)) 
```

Check for NA's
```{r}
inv_asset %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```



```{r}
inv_asset %>% 
  # distinct(LOCATION)
  # distinct(INDICATOR) # GFCFASSET
  distinct(subject) # OTHMACHINEQT, CULTASSET, OTHBUILDING, FIXASSET, TRANSPEQT, DWELLING
  # distinct(MEASURE) # PC_GFCF
  # distinct(FREQUENCY) #A
  # distinct(`Flag Codes`) # NA, E, B
```


OTHMACHINEQT: Information and Communication Technology (ICT) equipment (computer software and databases, telecommunications equipment and computer hardware)

CULTASSET: cultivated biological resources (managed forests, livestock raised for milk production, etc.)

OTHBUILDING: other buildings and structures (roads, bridges, airfields, dams, etc.)

FIXASSET: intellectual property products (such as R&D, mineral exploration, software and databases, and literary and artistic originals, etc.)

TRANSPEQT: transport equipment (ships, trains, aircraft, etc.)

DWELLING: dwellings (excluding land)

##################################################################################################################################


__OECD Investment GFCF__


Read data
```{r}
gfcf <- read_csv(here("raw_data/OECD_Investment_GFCF_JHios.csv")) %>% 
  clean_names()

glimpse(gfcf)
```

Change time in datetime format
```{r}
gfcf <- gfcf %>%
  mutate(time = make_datetime(time)) 
```


Check for NA's
```{r}
gfcf %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```
The timestamps missing relate to the Annual growth index (AGRWTH) - not affecting the scope of this analysis 

```{r}
gfcf %>% 
  # distinct(LOCATION)
  # distinct(INDICATOR) # GFCF
  # distinct(SUBJECT) # TOT
  distinct(measure) # AGRWTH, MLN_USD, QGRWTH
  # distinct(FREQUENCY) #A, Q
  # distinct(`Flag Codes`) # NA, E, P, B, D
```

AGRWTH: Annual growth (%)
MLN_USD: Million US Dollars
QGRWTH: Quarterly growth rate (%)

##################################################################################################################################


Join investment by asset with GFCF data
```{r}
gfcf_light <- gfcf %>% 
  filter(measure == "MLN_USD") %>% 
  select(location, time, value) %>% 
  rename(gfcf = value)

inv_asset_usd <- inv_asset %>% 
  arrange(location, subject, time) %>% 
  left_join(gfcf_light, by = c("location", "time")) %>% 
  mutate(
    value_mil_usd = value * gfcf / 100
  )

```


OTHMACHINEQT: Information and Communication Technology (ICT) equipment (computer software and databases, telecommunications equipment and computer hardware)

CULTASSET: cultivated biological resources (managed forests, livestock raised for milk production, etc.)

OTHBUILDING: other buildings and structures (roads, bridges, airfields, dams, etc.)

FIXASSET: intellectual property products (such as R&D, mineral exploration, software and databases, and literary and artistic originals, etc.)

TRANSPEQT: transport equipment (ships, trains, aircraft, etc.)

DWELLING: dwellings (excluding land)



```{r}
inv_asset_usd %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(location %in% c("GBR")) %>%
  ggplot() +
  aes(x = time, y = value_mil_usd, colour = subject) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle("UK investment by asset") +
  labs(
    x = "\n Year", 
    y = "Investment ($MM) \n",
    colour = "Asset"
  ) 

```


G-7 investment by Asset (million USD)
```{r}
inv_asset_g7 <- inv_asset %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")
    ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    ict = OTHMACHINEQT,
    cultasset = CULTASSET,
    infrastuct = OTHBUILDING,
    intelprop = FIXASSET,
    transpeqt = TRANSPEQT,
    dwelling = DWELLING
  ) %>% 
  left_join(gfcf_light, by = c("location", "time")) %>% 
  mutate(
    ict_mil_usd = ict * gfcf / 100,
    cultasset_mil_usd = cultasset * gfcf / 100,
    infrastuct_mil_usd = infrastuct * gfcf / 100,
    intelprop_mil_usd = intelprop * gfcf / 100,
    transpeqt_mil_usd = transpeqt * gfcf / 100,
    dwelling_mil_usd = dwelling * gfcf / 100
  ) %>% 
  select(-gfcf, -ict, -cultasset, -infrastuct, -intelprop, -transpeqt, -dwelling) %>% 
  arrange(location, time)
```




#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


OECD Education Spending Expenditure


Read data
```{r}
edu_exp <- read_csv(here("raw_data/OECD_Public_Spending_on_Education_JHios.csv")) %>% 
  clean_names()

glimpse(edu_exp)
```

Change time in datetime format
```{r}
edu_exp <- edu_exp %>%
  mutate(time = make_datetime(time)) 
```

Check for NA's
```{r}
edu_exp %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


G-7 countries education expenditure (% GDP)
TRY : TeRtiarY
PRY_NTRY: PRimarY to post-secondary Non-TeRtiarY
PRY_TRY: PRimarY to TeRtiarY

View G-7 tertiary education (% GDP)
```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    subject == "TRY"
    ) %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries public spending on education",
    subtitle = "Tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "Expenditure (% of GDP) \n",
    colour = "Country"
  ) 
```

View G-7 primary to tertiary education (% GDP)
```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    subject == "PRY_TRY"
    ) %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries public spending on education",
    subtitle = "Primary to tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "Expenditure (% of GDP)\n",
    colour = "Country"
  ) 

```

View G-7 primary to post-secondary non-tertiary education (% GDP)
```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    subject == "PRY_NTRY"
    ) %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries public spending on education",
    subtitle = "Primary to post-secondary non-tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "Expenditure (% of GDP) \n",
    colour = "Country"
  ) 

```

UK education expenditure (% GDP)
TRY : TeRtiarY
PRY_NTRY: PRimarY to post-secondary Non-TeRtiarY
PRY_TRY: PRimarY to TeRtiarY

```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(location %in% c("GBR")) %>%
  ggplot() +
  aes(x = time, y = value, colour = subject) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle("UK public spending on education") +
  labs(
    x = "\n Year", 
    y = "Expenditure (% of GDP) \n",
    colour = "Education type"
  ) 

```


#################################################################################################################################

__GDP-derived expenditure in USD__

OECD_Gross_Domestic_Product_GDP

Read data
```{r}
gdp <- read_csv(here("raw_data/OECD_Gross_Domestic_Product_GDP_JHios.csv")) %>% 
  clean_names()

glimpse(gdp)
```

Change time in datetime format
```{r}
gdp <- gdp %>%
  mutate(time = make_datetime(time)) 
```

Check for NA's
```{r}
gdp %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
gdp %>% 
  # distinct(LOCATION)
  distinct(indicator) # GDP
  # distinct(SUBJECT) # TOT
  # distinct(MEASURE) # MLN_USD, USD_CAP
  # distinct(FREQUENCY) #A
  # distinct(`Flag Codes`) # NA, E, P, B, D
```

View data
```{r}
gdp %>%
  select(-c(indicator, subject, frequency, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "MLN_USD"
    ) %>%
  ggplot() +
  aes(x = time, y = value, group = location, color = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country GDP") +
  labs(
    x = "\n Year",
    y = "GDP ($MM) \n",
    colour = "Country"
  ) 
```




##################################################################################################################################


Join education expenditure with GDP data
```{r}
gdp_light <- gdp %>%
  filter(measure == "MLN_USD") %>%
  select(location, time, value) %>%
  rename(gdp = value)


edu_exp_usd <- edu_exp %>% 
  left_join(gdp_light, by = c("location", "time")) %>% 
  mutate(
    value_mil_usd = value * gdp / 100
  )

```


```{r}
edu_exp_usd %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(location %in% c("GBR")) %>%
  ggplot() +
  aes(x = time, y = value_mil_usd, colour = subject) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle("UK public spending on education") +
  labs(
    x = "\n Year", 
    y = "Expenditure ($MM) \n",
    colour = "Education type"
  ) 

```


G-7 expenditure on education
```{r}
edu_exp_g7 <- edu_exp %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")
    ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    try_pc_gdp = TRY,
    pry_ntry_pc_gdp = PRY_NTRY,
    pry_try_pc_gdp = PRY_TRY
  ) %>% 
  left_join(gdp_light, by = c("location", "time"))%>% 
  mutate(
    try_mil_usd = try_pc_gdp * gdp / 100,
    pry_ntry_mil_usd = pry_ntry_pc_gdp * gdp / 100,
    pry_try_mil_usd = pry_try_pc_gdp * gdp / 100
  ) %>% 
  select(-try_pc_gdp, -pry_ntry_pc_gdp, -pry_try_pc_gdp, -gdp)%>% 
  arrange(location, time)
```


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Compare productivity by industry in UK and EU Countries__

Load Data
```{r}
productivity_phw <- read_excel(here("raw_data/International_Labour_Productivity-Europe.xls"), sheet = "Table 1 R-proc")
productivity_growth <- read_excel(here("raw_data/International_Labour_Productivity-Europe.xls"), sheet = "Table 2 R-proc")


glimpse(productivity_phw)
glimpse(productivity_growth)
```


Check for NA values
```{r}
productivity_phw %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
productivity_growth %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```



Pivot data to long format
```{r}
tidy_productivity_phw <- productivity_phw %>%
  pivot_longer(-c(`A*10 (excl L)`, `NACE Industry`), names_to = "Country", values_to = "Output_per_hour") 

tidy_productivity_growth <- productivity_growth %>%
  pivot_longer(-c(`A*10 (excl L)`, `NACE Industry`), names_to = "Country", values_to = "Labour_Productivity_Growth") 


tidy_productivity_phw
tidy_productivity_growth
```



Comparison of large economies in Europe: UK, France, Germany
```{r}
tidy_productivity_phw %>% 
  filter(
    Country %in% c("United Kingdom", "France", "Germany")
  ) %>% 
  ggplot() +
  aes(
    x = `A*10 (excl L)`, 
    y = Output_per_hour,
    fill = Country
    ) +
  geom_col(position = "dodge") +
  scale_fill_brewer(palette = "Dark2") +
  ggtitle(
    "Productivity by industry",
    subtitle =  "(Years: 2014 - 2016)"
  ) +
  labs(
    x = "\n NACE Industry", 
    y = "Output per hour (€)"
  ) 
```
```{r}
tidy_productivity_phw %>% 
  distinct(`A*10 (excl L)`, `NACE Industry`)
```


```{r}
tidy_productivity_growth %>% 
  filter(
    Country %in% c("United Kingdom", "France", "Germany")
  ) %>% 
  ggplot() +
  aes(
    x = `A*10 (excl L)`, 
    y = Labour_Productivity_Growth,
    fill = Country
    ) +
  geom_col(position = "dodge") +
  scale_fill_brewer(palette = "Dark2") +
  ggtitle(
    "Productivity by industry",
    subtitle =  "(Years: 2014 - 2016)"
  ) +
  labs(
    x = "\n NACE Industry", 
    y = "Labour Productivity Growth (%)"
  ) 
```



#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Data for modelling__

```{r}
productivity <- gdp_phw_g7 %>% 
  left_join(edu_exp_g7, by = c("location", "time")) %>% 
  left_join(inv_asset_g7, by = c("location", "time")) 

glimpse(productivity)
```

Trim UK data
```{r}
prod_uk_trim <- productivity %>% 
  mutate(time = year(time)) %>%
  filter(
    location == "GBR",
    time >= 1995 & time <=2019
  ) %>% 
  select(
    gdp_phw_usd, 
    ict_mil_usd,
    cultasset_mil_usd,
    infrastuct_mil_usd,
    intelprop_mil_usd,
    transpeqt_mil_usd,
    dwelling_mil_usd
  ) %>% 
  mutate(
    ict_bil_usd = ict_mil_usd / 1000,
    cultasset_bil_usd = cultasset_mil_usd / 1000,
    infrastuct_bil_usd = infrastuct_mil_usd / 1000,
    intelprop_bil_usd = intelprop_mil_usd / 1000,
    transpeqt_bil_usd = transpeqt_mil_usd / 1000,
    dwelling_bil_usd = dwelling_mil_usd / 1000
  ) %>% 
  select(
    -ict_mil_usd,
    -cultasset_mil_usd,
    -infrastuct_mil_usd,
    -intelprop_mil_usd,
    -transpeqt_mil_usd,
    -dwelling_mil_usd
  )
```



Check for aliases
```{r}
alias(lm(gdp_phw_usd ~ ., data = prod_uk_trim))
```


Call libraries for linear regression modelling 
```{r}
library(GGally)
library(ggfortify)
library(modelr)
```


Check for correlations in data
```{r}
ggpairs(prod_uk_trim)
```

#################################################################################################################################
#################################################################################################################################


__Automated modelling__

```{r}
library(glmulti)
glmulti_fit <- glmulti(
  gdp_phw_usd ~ ., 
  data = prod_uk_trim,
  level = 2, # 2 = include pairwise interactions, 1 = main effects only (main effect = no pairwise interactions)
  minsize = 0, # no min size of model
  maxsize = 6, # -1 = no max size of model
  marginality = TRUE, # marginality here means the same as 'strongly hierarchical' interactions, i.e. include pairwise interactions only if both predictors present in the model as main effects.
  method = "g", # the problem is too large for exhaustive search, so search using a genetic algorithm
  crit = bic, # criteria for model selection is BIC value (lower is better)
  plotty = FALSE, # don't plot models as function runs
  report = TRUE, # do produce reports as function runs
  confsetsize = 100, # return best 100 solutions
  fitfunction = lm # fit using the `lm` function
)
```
Summary of glmulti results
```{r}
summary(glmulti_fit)
```

```{r}
# here is the best model (lowest BIC) from the glmulti run above
glmulti_fit@objects[1]


# if you want to see the other models
weightable(glmulti_fit)
```

```{r}
# View summary of the best model (lowest BIC) from the glmulti run above
mod_auto1 <- lm(gdp_phw_usd ~ 1 + cultasset_bil_usd + infrastuct_bil_usd +
                 intelprop_bil_usd + dwelling_bil_usd + 
                 infrastuct_bil_usd:cultasset_bil_usd + 
                 dwelling_bil_usd:infrastuct_bil_usd,
                   data = prod_uk_trim)

summary(mod_auto1)
```

```{r}
# let's see diagnostic plots
autoplot(mod_auto1)
```
The diagnostic plots don't look that great, and the `cultasset_bil_usd` coefficient is not statistically significant

Let's check what the other models calculated by the gmulti algorithm are like


```{r}
# View summary of the best model (lowest BIC) from the glmulti run above
mod_auto2 <- lm(gdp_phw_usd ~ 1 + infrastuct_bil_usd + intelprop_bil_usd +
                dwelling_bil_usd + dwelling_bil_usd:infrastuct_bil_usd,
                   data = prod_uk_trim)

summary(mod_auto2)
```

```{r}
# let's see diagnostic plots
autoplot(mod_auto2)
```


```{r}
# View summary of the best model (lowest BIC) from the glmulti run above
mod_auto3 <- lm(gdp_phw_usd ~ 1 + ict_bil_usd + cultasset_bil_usd +
                  infrastuct_bil_usd + dwelling_bil_usd + 
                  cultasset_bil_usd:ict_bil_usd + dwelling_bil_usd:infrastuct_bil_usd,
                   data = prod_uk_trim)

summary(mod_auto3)
```

```{r}
# let's see diagnostic plots
autoplot(mod_auto3)
```
The diagnostic plots don't look that great, although all predictor coefficients are statistically significant

model_auto2 is a good trade-off between accuracy and model parsimony

#################################################################################################################################


```{r}
library(relaimpo)

calc.relimp(mod_auto2, type = "lmg", rela = TRUE)
```



#################################################################################################################################
#################################################################################################################################

__K-fold cross validation__

Cross validation of manually selected model
```{r}
library(caret)
set.seed(765977)
# set up options for train function below
cv_10_fold <- trainControl(method = "cv", # cross-validation
                           number = 10, # 10-fold
                           savePredictions = TRUE) # save all predictions

model_6e_kfold <- train(gdp_phw_usd ~ dwelling_bil_usd + cultasset_bil_usd +
                          dwelling_bil_usd:cultasset_bil_usd + ict_bil_usd + 
                          infrastuct_bil_usd + ict_bil_usd:infrastuct_bil_usd,
                        data = prod_uk_trim,
                        trControl = cv_10_fold, # use options defined above
                        method = 'lm')
```

Cross validation of automatically selected model following some manipulation (mod_auto2)
```{r}
model_reduced_kfold <- train(gdp_phw_usd ~ 1 + infrastuct_bil_usd +
                               intelprop_bil_usd + dwelling_bil_usd + 
                               dwelling_bil_usd:infrastuct_bil_usd,
                             data = prod_uk_trim,
                             trControl = cv_10_fold, # use options defined above
                             method = 'lm')
```


```{r}
model_reduced_kfold$resample
```

```{r}
tibble(
  model = "automatically selected model, then reduced",
  RMSE = mean(model_reduced_kfold$resample$RMSE),
  Rsquared = mean(model_reduced_kfold$resample$Rsquared)
)
```






##############################################################################################################################
##############################################################################################################################
##############################################################################################################################
##############################################################################################################################
##############################################################################################################################
##############################################################################################################################
##############################################################################################################################
##############################################################################################################################
##############################################################################################################################
##############################################################################################################################
##############################################################################################################################
##############################################################################################################################
##############################################################################################################################
##############################################################################################################################
##############################################################################################################################





#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################













































