---
title: "R Notebook"
output: html_notebook
---


Call Libraries
```{r}
library(tidyverse)
library(janitor)
library(here)
```


__Labour_Productivity-OECD_Countries__

Read data
```{r}
gdp_phw <- read_csv(here("raw_data/OECD_GDP_per_Hour_Worked_JHios.csv")) %>% 
  clean_names()

glimpse(gdp_phw)
```

Check for NA values
```{r}
gdp_phw %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```

```{r}
gdp_phw %>% 
  distinct(location)
  # distinct(INDICATOR) # GFCFASSET
  # distinct(subject) # OTHMACHINEQT, CULTASSET, OTHBUILDING, FIXASSET, TRANSPEQT, DWELLING
  # distinct(MEASURE) # PC_GFCF
  # distinct(FREQUENCY) #A
  # distinct(`Flag Codes`) # NA, E, B
```


View data
```{r}
gdp_phw %>% 
  select(-c(indicator, subject, frequency, flag_codes)) %>% 
  filter(
    location %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", "FRA",
                 "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "NLD",
                 "NOR", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE", "CHE",
                 "GBR"),
    measure == "USD") %>% 
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  # scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "GDP per hour worked",
    subtitle =  "indicator is measured in USD (constant prices 2010 and PPPs)"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP per hour worked ($) \n"
  ) 
  
```

GDP per hour worked data
```{r}
gdp_phw_europe <- gdp_phw %>% 
  filter(
    location %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", "FRA",
                 "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "NLD",
                 "NOR", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE", "CHE",
                 "GBR"),
    measure == "USD"
  ) %>% 
  select(-c(indicator, frequency, measure, subject, flag_codes)) %>% 
  rename(gdp_phw_usd = value) 
  
```


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################

OECD Investment by Asset

Read data
```{r}
inv_asset <- read_csv(here("raw_data/OECD_Investment_by_Asset_JHios.csv")) %>% 
  clean_names()

glimpse(inv_asset)
```


Check for NA's
```{r}
inv_asset %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```



```{r}
inv_asset %>% 
  distinct(location)
  # distinct(INDICATOR) # GFCFASSET
  # distinct(subject) # OTHMACHINEQT, CULTASSET, OTHBUILDING, FIXASSET, TRANSPEQT, DWELLING
  # distinct(MEASURE) # PC_GFCF
  # distinct(FREQUENCY) #A
  # distinct(`Flag Codes`) # NA, E, B
```


OTHMACHINEQT: Information and Communication Technology (ICT) equipment (computer software and databases, telecommunications equipment and computer hardware)

CULTASSET: cultivated biological resources (managed forests, livestock raised for milk production, etc.)

OTHBUILDING: other buildings and structures (roads, bridges, airfields, dams, etc.)

FIXASSET: intellectual property products (such as R&D, mineral exploration, software and databases, and literary and artistic originals, etc.)

TRANSPEQT: transport equipment (ships, trains, aircraft, etc.)

DWELLING: dwellings (excluding land)


Cross country investment by Asset (% GFCF)
```{r}
inv_asset %>%
  select(-c(indicator, frequency, flag_codes)) %>%
  filter(
    location %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", "FRA",
                 "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "NLD",
                 "NOR", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE", "CHE",
                 "GBR"),
    # subject== "OTHMACHINEQT",
    # subject == "CULTASSET",
    # subject == "OTHBUILDING",
    subject == "FIXASSET",
    # subject == "TRANSPEQT",
    # subject == "DWELLING"
  ) %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  # scale_colour_brewer(palette = "Dark2") +
  ggtitle("Cross country investment by Asset") +
  labs(
    x = "\n Year", 
    y = "Investment (% GFCF) \n"
  ) 
```



investment by Asset (% GFCF)
```{r}
inv_asset_europe <- inv_asset %>%
  filter(
    location %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", "FRA",
                 "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "NLD",
                 "NOR", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE", "CHE",
                 "GBR"),
    ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    ict_pc_gfcf = OTHMACHINEQT,
    cultasset_pc_gfcf = CULTASSET,
    infrastuct_pc_gfcf = OTHBUILDING,
    intelprop_pc_gfcf = FIXASSET,
    transpeqt_pc_gfcf = TRANSPEQT,
    dwelling_pc_gfcf = DWELLING
  ) %>% 
  arrange(location, time)
```




##################################################################################################################################


OECD Investment GFCF


Read data
```{r}
gfcf <- read_csv(here("raw_data/OECD_Investment_GFCF_JHios.csv")) %>% 
  clean_names()

glimpse(gfcf)
```

```{r}
gfcf <- gfcf %>%
  mutate(time = as.numeric(time))
```


Check for NA's
```{r}
gfcf %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```
The timestamps missing relate to the Annual growth index (AGRWTH) - not affecting the scope of this analysis 

```{r}
gfcf %>% 
  distinct(location)
  # distinct(INDICATOR) # GFCF
  # distinct(SUBJECT) # TOT
  # distinct(measure) # AGRWTH, MLN_USD, QGRWTH
  # distinct(FREQUENCY) #A, Q
  # distinct(`Flag Codes`) # NA, E, P, B, D
```

AGRWTH: Annual growth (%)
MLN_USD: Million US Dollars
QGRWTH: Quarterly growth rate (%)

```{r}
gfcf %>%
  select(-c(indicator, frequency, subject, flag_codes)) %>%
  filter(
    location %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", "FRA",
                 "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "NLD",
                 "NOR", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE", "CHE",
                 "GBR"),
    measure == "MLN_USD"
    ) %>%
  ggplot() +
  aes(x = time, y = value, color = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  # scale_colour_brewer(palette = "Dark2") +
  ggtitle("Cross country investment by Asset") +
  labs(
    x = "\n Year", 
    y = "GFCF ($MM) \n"
  ) +
  scale_x_continuous(breaks = seq(from = 1960, to = 2020, by = 10))
```


GFCF data (mln USD)
```{r}
gfcf_europe <- gfcf %>% 
  filter(
    location %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", "FRA",
                 "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "NLD",
                 "NOR", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE", "CHE",
                 "GBR"),
    measure == "MLN_USD"
  ) %>% 
  select(location, time, value) %>% 
  rename(gfcf_mln_usd = value)
```



#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


OECD Education Spending Expenditure


Read data
```{r}
edu_exp <- read_csv(here("raw_data/OECD_Public_Spending_on_Education_JHios.csv")) %>% 
  clean_names()

glimpse(edu_exp)
```



Check for NA's
```{r}
edu_exp %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```

```{r}
edu_exp %>% 
  distinct(location)
  # distinct(INDICATOR) # 
  # distinct(SUBJECT) # 
  # distinct(measure) # 
  # distinct(FREQUENCY) #
  # distinct(`Flag Codes`) #
```



UK education expenditure (% GDP)
TRY : TeRtiarY
PRY_NTRY: PRimarY to post-secondary Non-TeRtiarY
PRY_TRY: PRimarY to TeRtiarY

```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(location %in% c("GBR")) %>%
  ggplot() +
  aes(x = time, y = value, colour = subject) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle("UK education expenditure") +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```

expenditure on education (% GDP)
```{r}
edu_exp_europe <- edu_exp %>%
  filter(
    location %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", "FRA",
                 "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "NLD",
                 "NOR", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE", "CHE",
                 "GBR")
    ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    try_pc_gdp = TRY,
    pry_ntry_pc_gdp = PRY_NTRY,
    pry_try_pc_gdp = PRY_TRY
  ) %>%
  arrange(location, time)
```


#################################################################################################################################

__GDP-derived expenditure in USD__

OECD_Gross_Domestic_Product_GDP

Read data
```{r}
gdp <- read_csv(here("raw_data/OECD_Gross_Domestic_Product_GDP_JHios.csv")) %>% 
  clean_names()

glimpse(gdp)
```

Check for NA's
```{r}
gdp %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
gdp %>% 
  distinct(location)
  # distinct(indicator) # GDP
  # distinct(SUBJECT) # TOT
  # distinct(MEASURE) # MLN_USD, USD_CAP
  # distinct(FREQUENCY) #A
  # distinct(`Flag Codes`) # NA, E, P, B, D
```

View data
```{r}
gdp %>%
  select(-c(indicator, subject, frequency, flag_codes)) %>%
  filter(
    location %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", "FRA",
                 "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "NLD",
                 "NOR", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE", "CHE",
                 "GBR"),
    measure == "MLN_USD"
    ) %>%
  ggplot() +
  aes(x = time, y = value, group = location, color = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  # scale_colour_brewer(palette = "Dark2") +
  ggtitle("Cross country GDP") +
  labs(
    x = "\n Year",
    y = "GDP ($MM) \n"
  ) +
  scale_x_continuous(breaks = seq(from = 1960, to = 2020, by = 10))
```



GDP data (mln USD)
```{r}
gdp_europe <- gdp %>%
  filter(
    location %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", "FRA",
                 "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "NLD",
                 "NOR", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE", "CHE",
                 "GBR"),
    measure == "MLN_USD"
  ) %>% 
  select(location, time, value) %>%
  rename(gdp_mln_usd = value)
```

#################################################################################################################################
#################################################################################################################################
#################################################################################################################################

__OECD Hrs worked__

OECD_Hours_Worked

Read data
```{r}
hrswrkd <- read_csv(here("raw_data/OECD_Hours_Worked_JHios.csv")) %>% 
  clean_names()

glimpse(hrswrkd)
```

Check for NA's
```{r}
hrswrkd %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
hrswrkd %>% 
  distinct(location)
  # distinct(indicator) #
  # distinct(SUBJECT) # 
  # distinct(measure) # HR_WKD
  # distinct(FREQUENCY) #
  # distinct(`Flag Codes`) #
```

View data
```{r}
hrswrkd %>%
  select(-c(indicator, subject, frequency, flag_codes)) %>%
  filter(
    location %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", "FRA",
                 "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "NLD",
                 "NOR", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE", "CHE",
                 "GBR"),
    measure == "HR_WKD"
    ) %>%
  ggplot() +
  aes(x = time, y = value, group = location, color = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  # scale_colour_brewer(palette = "Dark2") +
  ggtitle("Cross country Hours Worked") +
  labs(
    x = "\n Year",
    y = "Hours Worked (hr) \n"
  ) +
  scale_x_continuous(breaks = seq(from = 1960, to = 2020, by = 10))
```



Hours Worked (hrs)
```{r}
hrswrkd_europe <- hrswrkd %>%
  filter(
    location %in% c("AUT", "BEL", "BGR", "HRV", "CZE", "DNK", "EST", "FIN", "FRA",
                 "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "NLD",
                 "NOR", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE", "CHE",
                 "GBR"),
    measure == "HR_WKD"
  ) %>% 
  select(location, time, value) %>%
  rename(hrs_wrkd = value)
```

#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__OECD data for clustering__


```{r}
productivity_data <- gdp_phw_europe %>% 
  left_join(edu_exp_europe, by = c("location", "time")) %>% 
  left_join(inv_asset_europe, by = c("location", "time")) %>% 
  left_join(gdp_europe, by = c("location", "time")) %>% 
  left_join(gfcf_europe, by = c("location", "time")) %>% 
  left_join(hrswrkd_europe, by = c("location", "time"))

glimpse(productivity_data)
```


```{r}
productivity_data %>% 
  filter(time == 2018)
```
Drop european countries that don't have data for 2018
```{r}
productivity_data %>% 
  filter(time == 2018) %>% 
  drop_na()
```
The loss of data is not significant



```{r}
productivity_data <- productivity_data %>% 
  filter(time == 2018) %>% 
  drop_na() %>% 
  mutate(
    try_phw_usd = try_pc_gdp * gdp_phw_usd / 100,
    pry_ntry_phw_usd = pry_ntry_pc_gdp * gdp_phw_usd / 100,
    pry_try_phw_usd = pry_try_pc_gdp * gdp_phw_usd / 100,
    ict_phw_usd = ict_pc_gfcf * gfcf_mln_usd / hrs_wrkd / 100,
    dwelling_phw_usd = dwelling_pc_gfcf * gfcf_mln_usd / hrs_wrkd / 100,
    infrastuct_phw_usd = infrastuct_pc_gfcf * gfcf_mln_usd / hrs_wrkd / 100,
    cultasset_phw_usd = cultasset_pc_gfcf * gfcf_mln_usd / hrs_wrkd / 100,
    transpeqt_phw_usd = transpeqt_pc_gfcf * gfcf_mln_usd / hrs_wrkd / 100,
    intelprop_phw_usd = intelprop_pc_gfcf * gfcf_mln_usd / hrs_wrkd / 100
  ) %>% 
  select(
    location,
    time,
    gdp_phw_usd,
    try_phw_usd, 
    pry_ntry_phw_usd, 
    pry_try_phw_usd, 
    ict_phw_usd, 
    dwelling_phw_usd, 
    infrastuct_phw_usd, 
    cultasset_phw_usd,
    transpeqt_phw_usd,
    intelprop_phw_usd
  )
```
#################################################################################################################################

Prepare data for dendrogram
```{r}
productivity_data <- productivity_data %>% 
  select(-time) %>% 
  column_to_rownames("location")
```

Standardise data
```{r}
productivity_data_scale <- productivity_data %>% 
  mutate(across(where(is.numeric), scale))

productivity_data_scale
```

Check data if mean==0 and std==1
```{r}
productivity_data_scale %>%
  pivot_longer(cols = everything(),
               names_to = "type", 
               values_to = "value") %>% #convert data to long format
  group_by(type) %>%
  summarise(mean = round(mean(value)), 
            sd = sd(value))
```


Clustering with K-means

```{r}
set.seed(340717)

clust_data_scale <- kmeans(productivity_data_scale, 
                        centers = 4, 
                        nstart = 25)

clust_data_scale
```

```{r}
library(broom)

tidy(clust_data_scale, 
     col.names = colnames(productivity_data_scale))
```

```{r}
augment(clust_data_scale, productivity_data)
```


Clustering Metrics

```{r}
glance(clust_data_scale)
```


```{r}
library(broom)

# Set min & max number of clusters want to look at 
max_k <- 15 

k_clusters <- tibble(k = 1:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(productivity_data_scale, .x, nstart = 25)), 
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, productivity_data)
  )

k_clusters
```

```{r}
clusterings <- k_clusters %>% 
  unnest(c(glanced))

clusterings
```


Choosing the number of clusters

__Elbow method__

```{r}
ggplot(clusterings, aes(x = k, y = tot.withinss)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = seq(1,20, by = 1))
```

If you want to use a function to do the plot above, use this:
```{r}
library(factoextra)

fviz_nbclust(productivity_data_scale,
             kmeans,
             method = "wss",
             nstart = 25)
```


__Silhouette coefficient__
```{r}
fviz_nbclust(productivity_data_scale, kmeans, method = "silhouette", nstart = 25)
```


__Gap statistic__
```{r}
fviz_nbclust(productivity_data_scale, kmeans, method = "gap_stat", nstart = 100) #would put nstart=25 if had more computing power
```


Method #2 indicates k=4 clusters and method #3 indicates k=9 clusters.

Let's see if k=4is sufficient

```{r}
clusterings %>% 
  unnest(cols = c(augmented)) %>% 
  filter(k == 4) %>% 
  ggplot(aes(x = gdp_phw_usd, y = ict_phw_usd, colour = .cluster, label = .rownames)) +
  geom_point(aes(color = .cluster)) +
  geom_text(hjust = 0, vjust = - 0.5, size = 3) +
  scale_colour_brewer(palette = "Dark2") 
```

```{r}
productivity_data %>% 
  names()
```


```{r}
clusterings %>% 
  unnest(cols = c(augmented)) %>% 
  filter(k == 4) %>% 
  ggplot(aes(x = ict_phw_usd, y = intelprop_phw_usd, colour = .cluster, label = .rownames)) +
  geom_point(aes(color = .cluster)) +
  geom_text(hjust = 0, vjust = - 0.5, size = 3) +
  scale_colour_brewer(palette = "Dark2") 
```


























































