---
title: "R Notebook"
output: html_notebook
---


Call Libraries
```{r}
library(tidyverse)
library(janitor)
library(here)
library(lubridate)
```


__Labour_Productivity-OECD_Countries__

Read data
```{r}
gdp_phw <- read_csv(here("raw_data/OECD_GDP_per_Hour_Worked_JHios.csv")) %>% 
  clean_names()

glimpse(gdp_phw)
```

Change time in datetime format
```{r}
gdp_phw <- gdp_phw %>%
  mutate(time = make_datetime(time)) 
```

Check for NA values
```{r}
gdp_phw %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


View data
```{r}
gdp_phw %>% 
  select(-c(indicator, subject, frequency, flag_codes)) %>% 
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "USD") %>% 
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "GDP per hour worked",
    subtitle =  "indicator is measured in USD (constant prices 2010 and PPPs)"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP per hour worked ($) \n"
  ) 
  
```

G-7 GDP per hour worked data
```{r}
gdp_phw_g7 <- gdp_phw %>% 
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "USD"
  ) %>% 
  select(-c(indicator, frequency, measure, subject, flag_codes)) %>% 
  rename(gdp_phw_usd = value) 
  
```


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################

OECD Investment by Asset

Read data
```{r}
inv_asset <- read_csv(here("raw_data/OECD_Investment_by_Asset_JHios.csv")) %>% 
  clean_names()

glimpse(inv_asset)
```

Change time in datetime format
```{r}
inv_asset <- inv_asset %>%
  mutate(time = make_datetime(time)) 
```

Check for NA's
```{r}
inv_asset %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```



```{r}
inv_asset %>% 
  # distinct(LOCATION)
  # distinct(INDICATOR) # GFCFASSET
  distinct(subject) # OTHMACHINEQT, CULTASSET, OTHBUILDING, FIXASSET, TRANSPEQT, DWELLING
  # distinct(MEASURE) # PC_GFCF
  # distinct(FREQUENCY) #A
  # distinct(`Flag Codes`) # NA, E, B
```


OTHMACHINEQT: Information and Communication Technology (ICT) equipment (computer software and databases, telecommunications equipment and computer hardware)

CULTASSET: cultivated biological resources (managed forests, livestock raised for milk production, etc.)

OTHBUILDING: other buildings and structures (roads, bridges, airfields, dams, etc.)

FIXASSET: intellectual property products (such as R&D, mineral exploration, software and databases, and literary and artistic originals, etc.)

TRANSPEQT: transport equipment (ships, trains, aircraft, etc.)

DWELLING: dwellings (excluding land)


G-7 Cross country investment by Asset (% GFCF)
```{r}
inv_asset %>%
  select(-c(indicator, frequency, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # subject== "OTHMACHINEQT",
    # subject == "CULTASSET",
    # subject == "OTHBUILDING",
    subject == "FIXASSET",
    # subject == "TRANSPEQT",
    # subject == "DWELLING"
  ) %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country investment by Asset") +
  labs(
    x = "\n Year", 
    y = "Investment (% GFCF) \n"
  ) 
```

##################################################################################################################################


OECD Investment GFCF


Read data
```{r}
gfcf <- read_csv(here("raw_data/OECD_Investment_GFCF_JHios.csv")) %>% 
  clean_names()

glimpse(gfcf)
```

Change time in datetime format
```{r}
gfcf <- gfcf %>%
  mutate(time = make_datetime(time)) 
```


Check for NA's
```{r}
gfcf %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```
The timestamps missing relate to the Annual growth index (AGRWTH) - not affecting the scope of this analysis 

```{r}
gfcf %>% 
  # distinct(LOCATION)
  # distinct(INDICATOR) # GFCF
  # distinct(SUBJECT) # TOT
  distinct(measure) # AGRWTH, MLN_USD, QGRWTH
  # distinct(FREQUENCY) #A, Q
  # distinct(`Flag Codes`) # NA, E, P, B, D
```

AGRWTH: Annual growth (%)
MLN_USD: Million US Dollars
QGRWTH: Quarterly growth rate (%)

```{r}
gfcf %>%
  select(-c(indicator, frequency, subject, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "MLN_USD"
    ) %>%
  ggplot() +
  aes(x = time, y = value, color = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country investment by Asset") +
  labs(
    x = "\n Year", 
    y = "GFCF ($MM) \n"
  ) 
```


##################################################################################################################################


Join investment by asset with GFCF data
```{r}
gfcf_light <- gfcf %>% 
  filter(measure == "MLN_USD") %>% 
  select(location, time, value) %>% 
  rename(gfcf = value)

inv_asset_usd <- inv_asset %>% 
  arrange(location, subject, time) %>% 
  left_join(gfcf_light, by = c("location", "time")) %>% 
  mutate(
    value_mil_usd = value * gfcf / 100
  )

```



G-7 Cross country investment by Asset (million USD)
```{r}
inv_asset_usd %>%
  select(-c(indicator, frequency, measure, flag_codes, value, gfcf)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # subject == "OTHMACHINEQT",
    # subject == "CULTASSET",
    # subject == "OTHBUILDING",
    subject == "FIXASSET",
    # subject == "TRANSPEQT",
    # subject == "DWELLING"
  ) %>%
  ggplot() +
  aes(x = time, y = value_mil_usd, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country investment by Asset") +
  labs(
    x = "\n Year", 
    y = "Investment ($MM) \n"
  ) 
```
OTHMACHINEQT: Information and Communication Technology (ICT) equipment (computer software and databases, telecommunications equipment and computer hardware)

CULTASSET: cultivated biological resources (managed forests, livestock raised for milk production, etc.)

OTHBUILDING: other buildings and structures (roads, bridges, airfields, dams, etc.)

FIXASSET: intellectual property products (such as R&D, mineral exploration, software and databases, and literary and artistic originals, etc.)

TRANSPEQT: transport equipment (ships, trains, aircraft, etc.)

DWELLING: dwellings (excluding land)



```{r}
inv_asset_usd %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(location %in% c("GBR")) %>%
  ggplot() +
  aes(x = time, y = value_mil_usd, colour = subject) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle("UK investment by asset") +
  labs(
    x = "\n Year", 
    y = "Investment ($MM) \n"
  ) 

```


G-7 investment by Asset (million USD)
```{r}
inv_asset_g7 <- inv_asset %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")
    ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    ict = OTHMACHINEQT,
    cultasset = CULTASSET,
    infrastuct = OTHBUILDING,
    intelprop = FIXASSET,
    transpeqt = TRANSPEQT,
    dwelling = DWELLING
  ) %>% 
  left_join(gfcf_light, by = c("location", "time")) %>% 
  mutate(
    ict_mil_usd = ict * gfcf / 100,
    cultasset_mil_usd = cultasset * gfcf / 100,
    infrastuct_mil_usd = infrastuct * gfcf / 100,
    intelprop_mil_usd = intelprop * gfcf / 100,
    transpeqt_mil_usd = transpeqt * gfcf / 100,
    dwelling_mil_usd = dwelling * gfcf / 100
  ) %>% 
  select(-gfcf, -ict, -cultasset, -infrastuct, -intelprop, -transpeqt, -dwelling) %>% 
  arrange(location, time)
```


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


OECD Education Spending Expenditure


Read data
```{r}
edu_exp <- read_csv(here("raw_data/OECD_Public_Spending_on_Education_JHios.csv")) %>% 
  clean_names()

glimpse(edu_exp)
```

Change time in datetime format
```{r}
edu_exp <- edu_exp %>%
  mutate(time = make_datetime(time)) 
```

Check for NA's
```{r}
edu_exp %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


G-7 countries education expenditure (% GDP)
TRY : TeRtiarY
PRY_NTRY: PRimarY to post-secondary Non-TeRtiarY
PRY_TRY: PRimarY to TeRtiarY

View G-7 tertiary education (% GDP)
```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    subject == "TRY"
    ) %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 
```

View G-7 primary to tertiary education (% GDP)
```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    subject == "PRY_TRY"
    ) %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Primary to tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```

View G-7 primary to post-secondary non-tertiary education (% GDP)
```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    subject == "PRY_NTRY"
    ) %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Primary to post-secondary non-tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```

UK education expenditure (% GDP)
TRY : TeRtiarY
PRY_NTRY: PRimarY to post-secondary Non-TeRtiarY
PRY_TRY: PRimarY to TeRtiarY

```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(location %in% c("GBR")) %>%
  ggplot() +
  aes(x = time, y = value, colour = subject) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle("UK education expenditure") +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```


#################################################################################################################################

__GDP-derived expenditure in USD__

OECD_Gross_Domestic_Product_GDP

Read data
```{r}
gdp <- read_csv(here("raw_data/OECD_Gross_Domestic_Product_GDP_JHios.csv")) %>% 
  clean_names()

glimpse(gdp)
```

Change time in datetime format
```{r}
gdp <- gdp %>%
  mutate(time = make_datetime(time)) 
```

Check for NA's
```{r}
gdp %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
gdp %>% 
  # distinct(LOCATION)
  distinct(indicator) # GDP
  # distinct(SUBJECT) # TOT
  # distinct(MEASURE) # MLN_USD, USD_CAP
  # distinct(FREQUENCY) #A
  # distinct(`Flag Codes`) # NA, E, P, B, D
```

View data
```{r}
gdp %>%
  select(-c(indicator, subject, frequency, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "MLN_USD"
    ) %>%
  ggplot() +
  aes(x = time, y = value, group = location, color = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country GDP") +
  labs(
    x = "\n Year",
    y = "GDP ($MM) \n"
  ) 
```




##################################################################################################################################


Join education expenditure with GDP data
```{r}
gdp_light <- gdp %>%
  filter(measure == "MLN_USD") %>%
  select(location, time, value) %>%
  rename(gdp = value)


edu_exp_usd <- edu_exp %>% 
  left_join(gdp_light, by = c("location", "time")) %>% 
  mutate(
    value_mil_usd = value * gdp / 100
  )

```


```{r}
edu_exp_usd %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(location %in% c("GBR")) %>%
  ggplot() +
  aes(x = time, y = value_mil_usd, colour = subject) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle("UK education expenditure") +
  labs(
    x = "\n Year", 
    y = "GDP ($MM) \n"
  ) 

```


G-7 expenditure on education
```{r}
edu_exp_g7 <- edu_exp %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")
    ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    try_pc_gdp = TRY,
    pry_ntry_pc_gdp = PRY_NTRY,
    pry_try_pc_gdp = PRY_TRY
  ) %>% 
  left_join(gdp_light, by = c("location", "time"))%>% 
  mutate(
    try_mil_usd = try_pc_gdp * gdp / 100,
    pry_ntry_mil_usd = pry_ntry_pc_gdp * gdp / 100,
    pry_try_mil_usd = pry_try_pc_gdp * gdp / 100
  ) %>% 
  select(-try_pc_gdp, -pry_ntry_pc_gdp, -pry_try_pc_gdp, -gdp)%>% 
  arrange(location, time)
```


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Data for modelling__

```{r}
productivity <- gdp_phw_g7 %>% 
  left_join(edu_exp_g7, by = c("location", "time")) %>% 
  left_join(inv_asset_g7, by = c("location", "time")) 

glimpse(productivity)
```

Trim UK data
```{r}
prod_uk_trim <- productivity %>% 
  mutate(time = year(time)) %>%
  filter(
    location == "GBR",
    time >= 1995 & time <=2019
  ) %>% 
  select(
    gdp_phw_usd, 
    ict_mil_usd,
    cultasset_mil_usd,
    infrastuct_mil_usd,
    intelprop_mil_usd,
    transpeqt_mil_usd,
    dwelling_mil_usd
  ) %>% 
  mutate(
    ict_bil_usd = ict_mil_usd / 1000,
    cultasset_bil_usd = cultasset_mil_usd / 1000,
    infrastuct_bil_usd = infrastuct_mil_usd / 1000,
    intelprop_bil_usd = intelprop_mil_usd / 1000,
    transpeqt_bil_usd = transpeqt_mil_usd / 1000,
    dwelling_bil_usd = dwelling_mil_usd / 1000
  ) %>% 
  select(
    -ict_mil_usd,
    -cultasset_mil_usd,
    -infrastuct_mil_usd,
    -intelprop_mil_usd,
    -transpeqt_mil_usd,
    -dwelling_mil_usd
  )
```



Check for aliases
```{r}
alias(lm(gdp_phw_usd ~ ., data = prod_uk_trim))
```


Call libraries for linear regression modelling 
```{r}
library(GGally)
library(ggfortify)
library(modelr)
```


Check for correlations in data
```{r}
ggpairs(prod_uk_trim)
```

#################################################################################################################################

Simple linear regression

Response: gdp_phw_usd

Predictors (tentative):
- dwelling
- infrastruct
- intelprop_bil_usd


```{r}
prod_uk_trim %>%
  ggplot(aes(x = dwelling_bil_usd, y = gdp_phw_usd)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```
Goodness-of-fit diagnostics
```{r}
model_1 <- lm(gdp_phw_usd ~ dwelling_bil_usd, data = prod_uk_trim)

autoplot(model_1) #diagnostics
```

```{r}
summary(model_1)
```

#################################################################################################################################

Check of second candidate predictor 
Goodness-of-fit diagnostics
```{r}
model_1b <- lm(gdp_phw_usd ~ infrastuct_bil_usd, data = prod_uk_trim)

autoplot(model_1b) #diagnostics
```
```{r}
summary(model_1b)
```
#################################################################################################################################

Check of third candidate predictor 
Goodness-of-fit diagnostics
```{r}
model_1c <- lm(gdp_phw_usd ~ intelprop_bil_usd, data = prod_uk_trim)

autoplot(model_1c) #diagnostics
```

```{r}
summary(model_1c)
```

Based on the above results we can stick to `dwelling_bil_usd` and model_1


#################################################################################################################################

- Adding a second predictor to the model

Calculate residuals
```{r}
prod_uk_remaining_resid <- prod_uk_trim %>%
  add_residuals(model_1) %>% 
  select(-c(gdp_phw_usd, dwelling_bil_usd))


prod_uk_remaining_resid %>%
  ggpairs()
```

It seems that `cultasset_bil_usd` is a good candidate for a second predictor followed by `infrastuct_bil_usd` and `ict_bil_usd`

#################################################################################################################################


Model with `cultasset_bil_usd` (model_2a)
```{r}
model_2a <- lm(gdp_phw_usd ~ dwelling_bil_usd + cultasset_bil_usd, data = prod_uk_trim)

autoplot(model_2a) #diagnostics
```

```{r}
summary(model_2a)
```

The `cultasset_bil_usd`  regression coefficient is not statistically significant 


#################################################################################################################################

Model with `inland_bil_usd` (model_2b)
```{r}
model_2b <- lm(gdp_phw_usd ~ dwelling_bil_usd + infrastuct_bil_usd, data = prod_uk_trim)

autoplot(model_2b) #diagnostics
```

```{r}
summary(model_2b)
```

Including regressor `infrastuct_bil_usd` is not improving at all the predictive power of the model and the regression coeffs are not looking good.

#################################################################################################################################

Model with `ict_bil_usd` (model_2c)
```{r}
model_2c <- lm(gdp_phw_usd ~ dwelling_bil_usd + ict_bil_usd, data = prod_uk_trim)

autoplot(model_2c) #diagnostics
```


```{r}
summary(model_2c)
```
Including regressor `ict_bil_usd` is not improving at all the predictive power of the model and the regression coeffs are not looking good.

#################################################################################################################################

- Adding a third predictor to the model

Let's see if adding an interaction makes any improvement in our model (model_2a).

Check for including in the model  potential interactions between predictors
```{r}
coplot(gdp_phw_usd ~ dwelling_bil_usd | cultasset_bil_usd,
       rows = 1,
       panel = function(x, y, ...){
         points(x, y)
         abline(lm(y ~ x), col = "blue")
       },
       data = prod_uk_trim)
```
Not so strong evidence that interaction term `dwelling_bil_usd:cultasset_bil_usd` will contribute significantly

Let's try it though to see how it goes
#################################################################################################################################

Model with interaction term `dwelling_bil_usd:cultasset_bil_usd` included (model_3a)
```{r}
model_3a <- lm(gdp_phw_usd ~ dwelling_bil_usd + cultasset_bil_usd + 
                 dwelling_bil_usd:cultasset_bil_usd, data = prod_uk_trim)

autoplot(model_3a) #diagnostics
```

```{r}
summary(model_3a)
```
Adding the interaction term had a significant impact on the model performance!!!


#################################################################################################################################

- Adding a fourth predictor to the model

Calculate residuals
```{r}
prod_uk_remaining_resid <- prod_uk_trim %>%
  add_residuals(model_3a) %>% 
  select(-c(gdp_phw_usd, dwelling_bil_usd, cultasset_bil_usd))


prod_uk_remaining_resid %>%
  ggpairs()
```

It seems that `ict_bil_usd` is a good candidate for a fourth predictor followed by `infrastuct_bil_usd`


#################################################################################################################################

Model with `ict_bil_usd` (model_4a)
```{r}
model_4a <- lm(gdp_phw_usd ~ dwelling_bil_usd + cultasset_bil_usd + 
                 dwelling_bil_usd:cultasset_bil_usd + ict_bil_usd,
               data = prod_uk_trim)

autoplot(model_4a) #diagnostics
```


```{r}
summary(model_4a)
```
#################################################################################################################################


Model with `infrastuct_bil_usd` (model_4b)
```{r}
model_4b <- lm(gdp_phw_usd ~ dwelling_bil_usd + cultasset_bil_usd + 
                 dwelling_bil_usd:cultasset_bil_usd + infrastuct_bil_usd,
               data = prod_uk_trim)

autoplot(model_4b) #diagnostics
```



```{r}
summary(model_4b)
```

We carry on with model_4a as it is marginally better


#################################################################################################################################

- Adding a fifth predictor to the model

Calculate residuals
```{r}
prod_uk_remaining_resid <- prod_uk_trim %>%
  add_residuals(model_4a) %>% 
  select(-c(gdp_phw_usd, dwelling_bil_usd, cultasset_bil_usd, ict_bil_usd))


prod_uk_remaining_resid %>%
  ggpairs()
```

It seems that `transpeqt_bil_usd` is a good candidate for a fifth predictor,`ifrastruct_bil_usd` is not so likely  

#################################################################################################################################

Model with `transpeqt_bil_usd` (model_5a)
```{r}
model_5a <- lm(gdp_phw_usd ~ dwelling_bil_usd + cultasset_bil_usd + 
                 dwelling_bil_usd:cultasset_bil_usd + ict_bil_usd +
                 transpeqt_bil_usd, data = prod_uk_trim)

autoplot(model_5a) #diagnostics
```


```{r}
summary(model_5a)
```
#################################################################################################################################

Model with `ifrastruct_bil_usd` (model_5b)
```{r}
model_5b <- lm(gdp_phw_usd ~ dwelling_bil_usd + cultasset_bil_usd + 
                 dwelling_bil_usd:cultasset_bil_usd + ict_bil_usd +
                 infrastuct_bil_usd, data = prod_uk_trim)

autoplot(model_5b) #diagnostics
```


```{r}
summary(model_5b)
```

We carry on with model_5b as it is better than model_5a

#################################################################################################################################

- Adding a sixth predictor to the model

Calculate residuals
```{r}
prod_uk_remaining_resid <- prod_uk_trim %>%
  add_residuals(model_5b) %>% 
  select(-c(gdp_phw_usd, dwelling_bil_usd, cultasset_bil_usd, ict_bil_usd, infrastuct_bil_usd))


prod_uk_remaining_resid %>%
  ggpairs()
```

Candidates for including in the model in order of importance are: `intelprop_bil_usd` and `transpeqt_bil_usd`

#################################################################################################################################

Model with `intelprop_bil_usd` (model_6a)
```{r}
model_6a <- lm(gdp_phw_usd ~ dwelling_bil_usd + cultasset_bil_usd + 
                 dwelling_bil_usd:cultasset_bil_usd + ict_bil_usd +
                 infrastuct_bil_usd +intelprop_bil_usd, data = prod_uk_trim)

autoplot(model_6a) #diagnostics
```


```{r}
summary(model_6a)
```

#################################################################################################################################

Model with `intelprop_bil_usd` (model_6b)
```{r}
model_6b <- lm(gdp_phw_usd ~ dwelling_bil_usd + cultasset_bil_usd + 
                 dwelling_bil_usd:cultasset_bil_usd + ict_bil_usd +
                 infrastuct_bil_usd + transpeqt_bil_usd, data = prod_uk_trim)

autoplot(model_6b) #diagnostics
```


```{r}
summary(model_6b)
```

Check with ANOVA if it is worth including term `intelprop_bil_usd` (model_6a) in the model

```{r}
anova(model_5b, model_6a)
```
ANOVA results don't justify the addition of `intelprop_bil_usd` so we stay with model_5b


#################################################################################################################################

- Adding an interaction term in the model

Let's see if adding an interaction makes any improvement in our model (model_5b).

Check for including in the model  potential interactions between the predictors below
+ dwelling_bil_usd
+ cultasset_bil_usd 
+ ict_bil_usd
+ infrastuct_bil_usd


```{r}
coplot(gdp_phw_usd ~ dwelling_bil_usd | ict_bil_usd,
       rows = 1,
       panel = function(x, y, ...){
         points(x, y)
         abline(lm(y ~ x), col = "blue")
       },
       data = prod_uk_trim)
```
```{r}
coplot(gdp_phw_usd ~ dwelling_bil_usd | infrastuct_bil_usd,
       rows = 1,
       panel = function(x, y, ...){
         points(x, y)
         abline(lm(y ~ x), col = "blue")
       },
       data = prod_uk_trim)
```

```{r}
coplot(gdp_phw_usd ~ cultasset_bil_usd | ict_bil_usd,
       rows = 1,
       panel = function(x, y, ...){
         points(x, y)
         abline(lm(y ~ x), col = "blue")
       },
       data = prod_uk_trim)
```

```{r}
coplot(gdp_phw_usd ~ cultasset_bil_usd | infrastuct_bil_usd,
       rows = 1,
       panel = function(x, y, ...){
         points(x, y)
         abline(lm(y ~ x), col = "blue")
       },
       data = prod_uk_trim)
```

```{r}
coplot(gdp_phw_usd ~ ict_bil_usd | infrastuct_bil_usd,
       rows = 1,
       panel = function(x, y, ...){
         points(x, y)
         abline(lm(y ~ x), col = "blue")
       },
       data = prod_uk_trim)
```
The best candidate is likely to be: 
+ `cultasset_bil_usd:ict_bil_usd`
+ `cultasset_bil_usd:infrastuct_bil_usd`
+ `ict_bil_usd:infrastuct_bil_usd`

#################################################################################################################################

Model with `cultasset_bil_usd:ict_bil_usd` (model_6c)
```{r}
model_6c <- lm(gdp_phw_usd ~ dwelling_bil_usd + cultasset_bil_usd +
                 dwelling_bil_usd:cultasset_bil_usd + ict_bil_usd + 
                 infrastuct_bil_usd + cultasset_bil_usd:ict_bil_usd, 
               data = prod_uk_trim)

autoplot(model_6c) #diagnostics
```


```{r}
summary(model_6c)
```
#################################################################################################################################

Model with `cultasset_bil_usd:ict_bil_usd` (model_6d)
```{r}
model_6d <- lm(gdp_phw_usd ~ dwelling_bil_usd + cultasset_bil_usd +
                 dwelling_bil_usd:cultasset_bil_usd + ict_bil_usd + 
                 infrastuct_bil_usd + cultasset_bil_usd:infrastuct_bil_usd, 
               data = prod_uk_trim)

autoplot(model_6d) #diagnostics
```


```{r}
summary(model_6d)
```

#################################################################################################################################

Model with `ict_bil_usd:infrastuct_bil_usd` (model_6e)
```{r}
model_6e <- lm(gdp_phw_usd ~ dwelling_bil_usd + cultasset_bil_usd +
                 dwelling_bil_usd:cultasset_bil_usd + ict_bil_usd + 
                 infrastuct_bil_usd + ict_bil_usd:infrastuct_bil_usd, 
               data = prod_uk_trim)

autoplot(model_6e) #diagnostics
```



```{r}
summary(model_6e)
```


Check with ANOVA if the interaction terms are worth including in the model

```{r}
anova(model_5b, model_6c)
```

```{r}
anova(model_5b, model_6d)
```


```{r}
anova(model_5b, model_6e)
```

The model_6e is the best calculated so far

#################################################################################################################################

- Check if it is worth adding a seventh predictor to the model

Calculate residuals
```{r}
prod_uk_remaining_resid <- prod_uk_trim %>%
  add_residuals(model_6e) %>% 
  select(-c(gdp_phw_usd, dwelling_bil_usd, cultasset_bil_usd, ict_bil_usd, infrastuct_bil_usd))


prod_uk_remaining_resid %>%
  ggpairs()
```
The residuals have very low correlation. The search can stop at this point.

################################################################################

Checking of relative importance of model terms
```{r}
library(relaimpo)

calc.relimp(model_6e, type = "lmg", rela = TRUE)

```

#################################################################################################################################
#################################################################################################################################


__Automated modelling__

```{r}
library(glmulti)
glmulti_fit <- glmulti(
  gdp_phw_usd ~ ., 
  data = prod_uk_trim,
  level = 2, # 2 = include pairwise interactions, 1 = main effects only (main effect = no pairwise interactions)
  minsize = 0, # no min size of model
  maxsize = 7, # -1 = no max size of model
  marginality = TRUE, # marginality here means the same as 'strongly hierarchical' interactions, i.e. include pairwise interactions only if both predictors present in the model as main effects.
  method = "g", # the problem is too large for exhaustive search, so search using a genetic algorithm
  crit = bic, # criteria for model selection is BIC value (lower is better)
  plotty = FALSE, # don't plot models as function runs
  report = TRUE, # do produce reports as function runs
  confsetsize = 100, # return best 100 solutions
  fitfunction = lm # fit using the `lm` function
)
```
Summary of glmulti results
```{r}
summary(glmulti_fit)
```

```{r}
# here is the best model (lowest BIC) from the glmulti run above
glmulti_fit@objects[1]


# if you want to see the other models
# weightable(glmulti_fit)
```


```{r}
# here is the best model (lowest BIC) from the glmulti run above
mod_autoJH <- lm(gdp_phw_usd ~ 1 + cultasset_bil_usd + 
                   infrastuct_bil_usd + intelprop_bil_usd + dwelling_bil_usd +
                   infrastuct_bil_usd:cultasset_bil_usd + 
                   intelprop_bil_usd:infrastuct_bil_usd + 
                   dwelling_bil_usd:infrastuct_bil_usd, 
                   data = prod_uk_trim)

summary(mod_autoJH)
```


```{r}
# here is the best model (lowest BIC) from the glmulti run above
mod_auto <- lm(gdp_phw_usd ~ 1 + cultasset_bil_usd + infrastuct_bil_usd +
                     intelprop_bil_usd + dwelling_bil_usd +
                     infrastuct_bil_usd:cultasset_bil_usd +
                     dwelling_bil_usd:infrastuct_bil_usd, 
                   data = prod_uk_trim)

summary(mod_auto)
```

```{r}
# let's see diagnostic plots
autoplot(mod_auto)
```
#################################################################################################################################
Run ANOVA test to compare current 6-predictor model (mod_auto) with 5-predictor model (model_reduced) by removing `cultasset_bil_usd`

```{r}
# here is the best model (lowest BIC) from the glmulti run above
mod_reduced_1 <- lm(gdp_phw_usd ~ 1 + infrastuct_bil_usd +
                     intelprop_bil_usd + dwelling_bil_usd +
                     infrastuct_bil_usd:cultasset_bil_usd +
                     dwelling_bil_usd:infrastuct_bil_usd, 
                   data = prod_uk_trim)

summary(mod_reduced_1)
```


```{r}
# let's see diagnostic plots
autoplot(mod_reduced_1)
```

Check model parsimony with ANOVA

```{r}
anova(mod_reduced_1, mod_auto)
```

#################################################################################################################################

Run ANOVA test to compare current 6-predictor model (mod_auto) with 5-predictor model (model_reduced) by removing `infrastuct_bil_usd:cultasset_bil_usd`

```{r}
# here is the best model (lowest BIC) from the glmulti run above
mod_reduced_2 <- lm(gdp_phw_usd ~ 1 + cultasset_bil_usd + infrastuct_bil_usd +
                     intelprop_bil_usd + dwelling_bil_usd +
                     dwelling_bil_usd:infrastuct_bil_usd, 
                   data = prod_uk_trim)

summary(mod_reduced_2)
```

#################################################################################################################################


```{r}
calc.relimp(mod_reduced, type = "lmg", rela = TRUE)
```



#################################################################################################################################
#################################################################################################################################

__K-fold cross validation__

Cross validation of manually selected model
```{r}
library(caret)
# set up options for train function below
cv_10_fold <- trainControl(method = "cv", # cross-validation
                           number = 10, # 10-fold
                           savePredictions = TRUE) # save all predictions

model_6e_kfold <- train(gdp_phw_usd ~ dwelling_bil_usd + cultasset_bil_usd +
                          dwelling_bil_usd:cultasset_bil_usd + ict_bil_usd + 
                          infrastuct_bil_usd + ict_bil_usd:infrastuct_bil_usd,
                        data = prod_uk_trim,
                        trControl = cv_10_fold, # use options defined above
                        method = 'lm')
```

```{r}
model_6e_kfold$resample
```


```{r}
tibble(
  model = "manually selected model_6e",
  RMSE = mean(model_6e_kfold$resample$RMSE),
  Rsquared = mean(model_6e_kfold$resample$Rsquared)
)
```


Cross validation of automatically selected model

```{r}
model_reduced_kfold <- train(gdp_phw_usd ~ infrastuct_bil_usd +
                          intelprop_bil_usd + dwelling_bil_usd +
                          infrastuct_bil_usd:cultasset_bil_usd +
                          dwelling_bil_usd:infrastuct_bil_usd,
                        data = prod_uk_trim,
                        trControl = cv_10_fold, # use options defined above
                        method = 'lm')
```


```{r}
model_reduced_kfold$resample
```

```{r}
tibble(
  model = "automatically selected model, then reduced",
  RMSE = mean(model_reduced_kfold$resample$RMSE),
  Rsquared = mean(model_reduced_kfold$resample$Rsquared)
)
```













