---
title: "R Notebook"
output: html_notebook
---

Call Libraries
```{r}
library(tidyverse)
library(janitor)
library(here)
library(readxl)
```


__Labour_Productivity-OECD_Countries__

Read data
```{r}
gdp_phw_OECD <- read_csv(here("raw_data/Labour_Productivity-OECD_Countries.csv")) 

glimpse(gdp_phw_OECD)
```


```{r}
gdp_phw_OECD %>% 
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, SUBJECT)) %>% 
  filter(
    # LOCATION %in% c("G-7", "EU28", "CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # LOCATION %in% c("G-7", "EU28", "GBR"),
    MEASURE == "USD") %>% 
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "GDP per hour worked",
    subtitle =  "indicator is measured in USD (constant prices 2010 and PPPs)"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP per hour worked ($) \n"
  ) 
  
```




#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Cross Country Gross Domestic Spending on R&D__

Read data
```{r}
gdexp_rd <- read_excel(here("raw_data/Cross_country_Gross_Domestic_Spending_on_R&D.xls")) 

glimpse(gdexp_rd)
```

G-7 countries gross domestic expenditure on R&D (Million USD)
```{r}
gdexp_rd %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, SUBJECT)) %>%
  filter(LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
         MEASURE == "MLN_USD") %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 countries gross domestic expenditure on R&D") +
  labs(
    x = "\n Year", 
    y = "Expenditure ($MM) \n"
  ) 
```
################################################################ KEEP THIS FIGURE!!!!
G-7 countries gross domestic expenditure on R&D (% GDP)
```{r}
gdexp_rd %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, SUBJECT)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # LOCATION %in% c( "FRA", "DEU", "USA", "GBR"),
    MEASURE == "PC_GDP"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 countries gross domestic expenditure on R&D") +
  labs(
    x = "\n Year", 
    y = "Expenditure (% of GDP) \n"
  ) 
```


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Compare investment between UK and other countries__


Cross country infrastructure investment

Read data
```{r}
infrastructure_investment <- read_excel(here("raw_data/Cross_country_infrastructure_investment.xls")) 

glimpse(infrastructure_investment)
```


G-7 Cross country infrastructure investment (Euros)
```{r}
infrastructure_investment %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # SUBJECT == "RAIL",
    # SUBJECT == "ROAD",
    # SUBJECT == "SEA",
    SUBJECT == "AIR",
    # SUBJECT == "ROAD",
    MEASURE == "EUR") %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country infrastructure investment") +
  labs(
    x = "\n Year", 
    y = "Investment (€) \n"
  ) 
```


G-7 Cross country infrastructure investment (% of GDP)
```{r}
infrastructure_investment %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    SUBJECT == "INLAND",
    MEASURE == "PC_GDP") %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "G-7 Cross country infrastructure investment",
    subtitle = "(Type: Inland)"
  ) +
  labs(
    x = "\n Year", 
    y = "Investment (% of GDP) \n"
  ) 
```



#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


OECD Tertiary Spending Expenditure


Read data
```{r}
education_expenditure <- read_excel(here("raw_data/OECD_Tertiary_Education_Expenditure.xlsx")) 

glimpse(education_expenditure)
```
```{r}
education_expenditure %>% 
  filter(LOCATION == "GBR")
```


Check for NA's
```{r}
education_expenditure %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
education_expenditure %>% 
  # distinct(LOCATION)
  # distinct(INDICATOR) # EDUPUBEXP
  # distinct(SUBJECT) # TRY, PRY_NTRY, PRY_TRY
  # distinct(MEASURE) # PC_GDP
  # distinct(FREQUENCY) #A
  distinct(`Flag Codes`) # NA, M
```


G-7 countries education expenditure (GDP percentage)
TRY : TeRtiarY
PRY_NTRY: PRimarY to post-secondary Non-TeRtiarY
PRY_TRY: PRimarY to TeRtiarY
```{r}
education_expenditure %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, MEASURE)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    SUBJECT == "TRY"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 
```

```{r}
education_expenditure %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, MEASURE)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    SUBJECT == "PRY_TRY"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Primary to Tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```

```{r}
education_expenditure %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, MEASURE)) %>%
  filter(
    LOCATION %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    SUBJECT == "PRY_NTRY"
    ) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = LOCATION) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Primary to post-secondary non-Tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```


```{r}
education_expenditure %>%
  select(-c(`Flag Codes`, INDICATOR, FREQUENCY, MEASURE)) %>%
  filter(LOCATION %in% c("GBR")) %>%
  ggplot() +
  aes(x = TIME, y = Value, colour = SUBJECT) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle("UK education expenditure") +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```



#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


```{r}
gdp_phw_uk <- gdp_phw_OECD %>% 
  filter(
    LOCATION ==  "GBR"
  ) %>% 
  select(MEASURE, TIME, Value) %>% 
  pivot_wider(names_from = MEASURE, values_from = Value) %>% 
  rename(
    gdp_usd = USD,
    gdp_idx2010 = IDX2010
    )

glimpse(gdp_phw_uk )
```


```{r}
rnd_uk <- gdexp_rd %>% 
  filter(
    LOCATION ==  "GBR"
  ) %>% 
  select(MEASURE, TIME, Value) %>% 
  pivot_wider(names_from = MEASURE, values_from = Value) %>% 
  mutate(MLN_USD = MLN_USD/1e3) %>%
  rename(
    rnd_billionusd = MLN_USD,
    rnd_pc_gdp = PC_GDP
  )

glimpse(rnd_uk)
```

```{r}
infr_inv_uk <- infrastructure_investment %>% 
  filter(
    LOCATION ==  "GBR"
  ) %>%
  select(SUBJECT, TIME, Value) %>% 
  pivot_wider(names_from = SUBJECT, values_from = Value) %>% 
  mutate(
    RAIL = RAIL/1e9,
    ROAD = ROAD/1e9,
    INLAND = INLAND,
    AIR = AIR/1e9,
    SEA = SEA/1e9
  ) %>%
  rename(
    rail_billioneuro = RAIL,
    road_billioneuro = ROAD,
    inland_pc_gdp = INLAND,
    air_billioneuro = AIR,
    sea_billioneuro = SEA
  )

glimpse(infr_inv_uk)
```


```{r}
edu_uk <- education_expenditure %>%
  filter(LOCATION ==  "GBR") %>% 
  pivot_wider(names_from = SUBJECT, values_from = Value) %>% 
  select(TIME, TRY, PRY_NTRY, PRY_TRY) %>% 
  rename(
    try_pc_gdp = TRY,
    pry_ntry_pc_gdp = PRY_NTRY,
    pry_try_pc_gdp = PRY_TRY
  ) 

glimpse(edu_uk)
```


```{r}
prod_uk <- gdp_phw_uk %>% 
  left_join(rnd_uk, by = "TIME") %>% 
  left_join(infr_inv_uk, by = "TIME") %>% 
  left_join(edu_uk, by = "TIME")

glimpse(prod_uk)
```


Investigate how the correlations are affected when a quantity originally expressed as % of GDP is transformed
into GDP USD (constant prices 2010 and PPPs)
```{r}
prod_uk2 <- prod_uk %>%
  mutate(
    inland_usd = inland_pc_gdp * gdp_usd,
    rnd_usd = rnd_pc_gdp * gdp_usd,
    try_usd = try_pc_gdp * gdp_usd,
    pry_ntry_usd = pry_ntry_pc_gdp * gdp_usd,
    pry_try_usd = pry_try_pc_gdp * gdp_usd,
  ) %>%
  select(
    TIME, 
    gdp_usd, 
    rnd_usd, 
    rnd_billionusd, 
    rail_billioneuro, 
    road_billioneuro, 
    inland_usd, 
    air_billioneuro,
    sea_billioneuro, 
    try_usd, 
    pry_ntry_usd, 
    pry_try_usd
  )
```




#################################################################################################################################
#################################################################################################################################
#################################################################################################################################



```{r}
prod_uk %>% 
ggplot() +
  aes(x = rnd_billionusd, y = gdp_usd, colour = TIME) +
   geom_point() +
  # scale_colour_gradient()
  # scale_colour_gradient(low = "gray0", high = "gray100")
  # geom_point(color = "steelblue") +
  geom_text(
    aes(label = TIME),
    nudge_x = 1.5,
    nudge_y = 0,
    size = 2.5
  ) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0)
```


```{r}
prod_uk %>% 
ggplot() +
  aes(x = rnd_pc_gdp, y = gdp_usd, colour = TIME) +
   geom_point() +
  # scale_colour_gradient()
  # scale_colour_gradient(low = "gray0", high = "gray100")
  # geom_point(color = "steelblue") +
  geom_text(
    aes(label = TIME),
    nudge_x = 0.075,
    nudge_y = 0,
    size = 2.5
  ) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0)
```



```{r}
prod_uk %>% 
ggplot() +
  aes(x = rail_billioneuro, y = gdp_usd, colour = TIME) +
   geom_point() +
  # scale_colour_gradient()
  # scale_colour_gradient(low = "gray0", high = "gray100")
  # geom_point(color = "steelblue") +
  geom_text(
    aes(label = TIME),
    nudge_x = 0.5,
    nudge_y = 0,
    size = 2.5
  ) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0)
```


```{r}
prod_uk %>% 
ggplot() +
  aes(x = road_billioneuro, y = gdp_usd, colour = TIME) +
   geom_point() +
  # scale_colour_gradient()
  # scale_colour_gradient(low = "gray0", high = "gray100")
  # geom_point(color = "steelblue") +
  geom_text(
    aes(label = TIME),
    nudge_x = 0.25,
    nudge_y = 0,
    size = 2.5
  ) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0)
```



```{r}
prod_uk %>% 
ggplot() +
  aes(x = inland_pc_gdp, y = gdp_usd, colour = TIME) +
   geom_point() +
  # scale_colour_gradient()
  # scale_colour_gradient(low = "gray0", high = "gray100")
  # geom_point(color = "steelblue") +
  geom_text(
    aes(label = TIME),
    nudge_x = 0.025,
    nudge_y = 0,
    size = 2.5
  ) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0)
```


```{r}
prod_uk %>% 
ggplot() +
  aes(x = air_billioneuro, y = gdp_usd, colour = TIME) +
   geom_point() +
  # scale_colour_gradient()
  # scale_colour_gradient(low = "gray0", high = "gray100")
  # geom_point(color = "steelblue") +
  geom_text(
    aes(label = TIME),
    nudge_x = 0.075,
    nudge_y = 0,
    size = 2.5
  ) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0)
```



```{r}
prod_uk %>% 
ggplot() +
  aes(x = sea_billioneuro, y = gdp_usd, colour = TIME) +
   geom_point() +
  # scale_colour_gradient()
  # scale_colour_gradient(low = "gray0", high = "gray100")
  # geom_point(color = "steelblue") +
  geom_text(
    aes(label = TIME),
    nudge_x = 0.015,
    nudge_y = 0,
    size = 2.5
  ) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0)
```




```{r}
prod_uk %>% 
ggplot() +
  aes(x = try_pc_gdp, y = gdp_usd, colour = TIME) +
   geom_point() +
  # scale_colour_gradient()
  # scale_colour_gradient(low = "gray0", high = "gray100")
  # geom_point(color = "steelblue") +
  geom_text(
    aes(label = TIME),
    nudge_x = 0.035,
    nudge_y = 0,
    size = 2.5
  ) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0)
```



```{r}
prod_uk %>% 
ggplot() +
  aes(x = pry_ntry_pc_gdp, y = gdp_usd, colour = TIME) +
   geom_point() +
  # scale_colour_gradient()
  # scale_colour_gradient(low = "gray0", high = "gray100")
  # geom_point(color = "steelblue") +
  geom_text(
    aes(label = TIME),
    nudge_x = 0.15,
    nudge_y = 0,
    size = 2.5
  ) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0)
```




```{r}
prod_uk %>% 
ggplot() +
  aes(x = pry_try_pc_gdp, y = gdp_usd, colour = TIME) +
   geom_point() +
  # scale_colour_gradient()
  # scale_colour_gradient(low = "gray0", high = "gray100")
  # geom_point(color = "steelblue") +
  geom_text(
    aes(label = TIME),
    nudge_x = 0.15,
    nudge_y = 0,
    size = 2.5
  ) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0)
```


```{r}
library(GGally)

prod_uk %>%
  select(-TIME, -gdp_idx2010) %>% 
  select(gdp_usd, rnd_billionusd:sea_billioneuro) %>% 
  ggscatmat()
```

```{r}
prod_uk %>%
  select(-TIME, -gdp_idx2010) %>% 
  select(-c(rnd_billionusd:sea_billioneuro)) %>% 
  ggscatmat()
```


```{r}
prod_uk %>% 
  select(-TIME, -gdp_idx2010) %>% 
  GGally::ggcorr(
    label = TRUE,
    label_size = 3, 
    label_round = 2, 
    label_alpha = TRUE,
    hjust = 1,
    layout.exp = 0.5
  )
```

```{r}
prod_uk
```




```{r}
prod_uk2 %>% 
  select(-TIME) %>% 
  GGally::ggcorr(
    label = TRUE,
    label_size = 3, 
    label_round = 2, 
    label_alpha = TRUE,
    hjust = 1,
    layout.exp = 0.5
  )
```







```{r}
prod_uk2 %>% 
ggplot() +
  aes(x = rnd_billionusd, y = gdp_usd, colour = TIME) +
   geom_point() +
  # scale_colour_gradient()
  # scale_colour_gradient(low = "gray0", high = "gray100")
  # geom_point(color = "steelblue") +
  geom_text(
    aes(label = TIME),
    nudge_x = 2.5,
    nudge_y = 0,
    size = 2.5
  ) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0)
```



```{r}
prod_uk2 %>% 
ggplot() +
  # aes(x = try_usd, y = gdp_usd, colour = TIME) +
  # aes(x = pry_ntry_usd, y = gdp_usd, colour = TIME) +
  aes(x = pry_try_usd, y = gdp_usd, colour = TIME) +
   geom_point() +
  # scale_colour_gradient()
  # scale_colour_gradient(low = "gray0", high = "gray100")
  # geom_point(color = "steelblue") +
  geom_text(
    aes(label = TIME),
    nudge_x = 5.0,
    nudge_y = 0,
    size = 2.5
  ) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0)
```













