---
title: "R Notebook"
output: html_notebook
---


Call Libraries
```{r}
library(tidyverse)
library(janitor)
library(here)
```


__Labour_Productivity-OECD_Countries__

Read data
```{r}
gdp_phw <- read_csv(here("raw_data/OECD_GDP_per_Hour_Worked_JHios.csv")) %>% 
  clean_names()

glimpse(gdp_phw)
```

Check for NA values
```{r}
gdp_phw %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


View data
```{r}
gdp_phw %>% 
  select(-c(indicator, subject, frequency, flag_codes)) %>% 
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "USD") %>% 
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "GDP per hour worked",
    subtitle =  "indicator is measured in USD (constant prices 2010 and PPPs)"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP per hour worked ($) \n"
  ) 
  
```

G-7 GDP per hour worked data
```{r}
gdp_phw_g7 <- gdp_phw %>% 
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "USD"
  ) %>% 
  select(-c(indicator, frequency, measure, subject, flag_codes)) %>% 
  rename(gdp_phw_usd = value) 
  
```


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Cross Country Gross Domestic Spending on R&D__

Read data
```{r}
gdexp_rnd <- read_csv(here("raw_data/OECD_Gross_Domestic_Spending_on_R&D_JHios.csv")) %>% 
  clean_names()

glimpse(gdexp_rnd)
```

G-7 countries gross domestic expenditure on R&D (Million USD)
```{r}
gdexp_rnd %>%
  select(-c(indicator, subject, frequency, flag_codes)) %>%
  filter(location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
         measure == "MLN_USD") %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 countries gross domestic expenditure on R&D") +
  labs(
    x = "\n Year", 
    y = "Expenditure ($MM) \n"
  ) 
```
################################################################ KEEP THIS FIGURE!!!!
G-7 countries gross domestic expenditure on R&D (% GDP)
```{r}
gdexp_rnd %>%
  select(-c(indicator, subject, frequency, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "PC_GDP"
    ) %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 countries gross domestic expenditure on R&D") +
  labs(
    x = "\n Year", 
    y = "Expenditure (% of GDP) \n"
  ) 
```

G-7 gross domestic expenditure on R&D (MLN USD) data
```{r}
gdexp_rnd_g7 <- gdexp_rnd %>%
  filter(location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
         measure == "MLN_USD") %>% 
  select(-c(indicator, frequency, measure, subject, flag_codes)) %>%
  rename(gdexp_rnd_mil_usd = value)
```


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Compare investment between UK and other countries__


Cross country infrastructure investment

Read data
```{r}
infr_inv <- read_csv(here("raw_data/OECD_Infrastructure_Investment_JHios.csv")) %>% 
  clean_names()

glimpse(infr_inv)
```


Check for NA's
```{r}
infr_inv %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
infr_inv %>% 
  distinct(subject, measure)
```



G-7 Cross country infrastructure investment (Euros)
```{r}
infr_inv %>%
  select(-c(indicator, frequency, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    # subject == "RAIL",
    # subject == "ROAD",
    # subject == "SEA",
    # subject == "AIR",
    subject == "INLANDWATER",
    measure == "EUR") %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country infrastructure investment") +
  labs(
    x = "\n Year", 
    y = "Investment (€) \n"
  ) 
```

G-7 Cross country infrastructure investment (% of GDP)
```{r}
infr_inv %>%
  select(-c(indicator, frequency, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    subject == "INLAND",
    measure == "PC_GDP") %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "G-7 Cross country infrastructure investment",
    subtitle = "(Type: Inland)"
  ) +
  labs(
    x = "\n Year", 
    y = "Investment (% of GDP) \n"
  ) 
```

##########################################################################################

OECD_Gross_Domestic_Product_GDP

Read data
```{r}
gdp <- read_csv(here("raw_data/OECD_Gross_Domestic_Product_GDP_JHios.csv")) %>% 
  clean_names()

glimpse(gdp)
```

Check for NA's
```{r}
gdp %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


```{r}
gdp %>% 
  # distinct(LOCATION)
  distinct(indicator) # GDP
  # distinct(SUBJECT) # TOT
  # distinct(MEASURE) # MLN_USD, USD_CAP
  # distinct(FREQUENCY) #A
  # distinct(`Flag Codes`) # NA, E, P, B, D
```

View data
```{r}
gdp %>%
  select(-c(indicator, frequency, subject, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    measure == "MLN_USD"
    ) %>%
  ggplot() +
  aes(x = time, y = value, group = location, color = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle("G-7 Cross country GDP") +
  labs(
    x = "\n Year",
    y = "GDP ($MM) \n"
  ) +
  scale_x_continuous(breaks = seq(from = 1960, to = 2020, by = 10))
```


```{r}
gdp_light <- gdp %>%
  filter(measure == "MLN_USD") %>%
  select(location, time, value) %>%
  rename(gdp = value)
```


```{r}
inv_inland_usd <- infr_inv %>%
  select(-c(indicator, frequency, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    subject == "INLAND",
    measure == "PC_GDP"
  ) %>%
  left_join(gdp_light, by = c("location", "time")) %>%
  mutate(
    value_mil_usd = value * gdp / 100
  )

inv_inland_usd
```


G-7 Cross country INLAND infrastructure investment ($MM)
```{r}
inv_inland_usd %>%
  select(-c(subject, measure, value, gdp)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")) %>%
  ggplot() +
  aes(x = time, y = value_mil_usd, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  ggtitle(
    "G-7 Cross country infrastructure investment",
    subtitle = "(Type: Inland)"
  ) +
  labs(
    x = "\n Year", 
    y = "Investment ($MM) \n"
  ) 
```

G-7 infrastructure investment data
```{r}
infr_inv_g7 <- infr_inv %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")
  ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  pivot_wider(names_from = subject, values_from = value) %>% 
  mutate(
    RAIL = RAIL/1e6,
    ROAD = ROAD/1e6,
    INLAND = INLAND,
    AIR = AIR/1e6,
    SEA = SEA/1e6,
    INLANDWATER = INLANDWATER/1e6
  ) %>%
  rename(
    rail_mil_eur = RAIL,
    road_mil_eur = ROAD,
    inland_pc_gdp = INLAND,
    air_mil_eur = AIR,
    sea_mil_eur = SEA,
    inlandwater_mil_eur = INLANDWATER
  ) %>% 
  left_join(gdp_light, by = c("location", "time")) %>% 
  mutate(
    inland_mil_usd = inland_pc_gdp * gdp / 100
  ) %>% 
  select(-inland_pc_gdp, -gdp)

```


```{r}
infr_inv %>%
  filter(
    location %in% c("GBR"),
    subject == "INLANDWATER"
  ) 
```


#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


OECD Education Spending Expenditure


Read data
```{r}
edu_exp <- read_csv(here("raw_data/OECD_Public_Spending_on_Education_JHios.csv")) %>% 
  clean_names()

glimpse(edu_exp)
```



Check for NA's
```{r}
edu_exp %>% 
  summarise(across(.cols = everything(),
                   .fns = ~sum(is.na(.x))))
```


G-7 countries education expenditure (GDP percentage)
TRY : TeRtiarY
PRY_NTRY: PRimarY to post-secondary Non-TeRtiarY
PRY_TRY: PRimarY to TeRtiarY
```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    subject == "TRY"
    ) %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 
```


```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    subject == "PRY_TRY"
    ) %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Primary to tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```


```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR"),
    subject == "PRY_NTRY"
    ) %>%
  ggplot() +
  aes(x = time, y = value, colour = location) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle(
    "G-7 countries education expenditure",
    subtitle = "Primary to post-secondary non-tertiary education"
  ) +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```


```{r}
edu_exp %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(location %in% c("GBR")) %>%
  ggplot() +
  aes(x = time, y = value, colour = subject) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle("UK education expenditure") +
  labs(
    x = "\n Year", 
    y = "GDP (%) \n"
  ) 

```

```{r}
edu_exp_usd <- edu_exp %>% 
  left_join(gdp_light, by = c("location", "time")) %>% 
  mutate(
    value_mil_usd = value * gdp / 100
  )

```


```{r}
edu_exp_usd %>%
  select(-c(indicator, frequency, measure, flag_codes)) %>%
  filter(location %in% c("GBR")) %>%
  ggplot() +
  aes(x = time, y = value_mil_usd, colour = subject) +
  geom_line(size = 0.75) +
  geom_point(size = 1.5) +
  scale_colour_brewer(palette = "Dark2") +
  # scale_colour_manual(values = cbb_palette) +
  ggtitle("UK education expenditure") +
  labs(
    x = "\n Year", 
    y = "GDP ($MM) \n"
  ) 

```



G-7 expenditure on education data 
```{r}
edu_exp_g7 <- edu_exp %>%
  filter(
    location %in% c("CAN", "FRA", "DEU", "ITA", "JPN", "USA", "GBR")
    ) %>% 
  select(-c(indicator, frequency, measure, flag_codes)) %>% 
  pivot_wider(names_from = subject, values_from = value) %>% 
  rename(
    try_pc_gdp = TRY,
    pry_ntry_pc_gdp = PRY_NTRY,
    pry_try_pc_gdp = PRY_TRY
  ) %>% 
  left_join(gdp_light, by = c("location", "time"))%>% 
  mutate(
    try_mil_usd = try_pc_gdp * gdp / 100,
    pry_ntry_mil_usd = pry_ntry_pc_gdp * gdp / 100,
    pry_try_mil_usd = pry_try_pc_gdp * gdp / 100
  ) %>% 
  select(-try_pc_gdp, -pry_ntry_pc_gdp, -pry_try_pc_gdp, -gdp)
```




#################################################################################################################################
#################################################################################################################################
#################################################################################################################################


__Data for modelling__

```{r}
productivity <- gdp_phw_g7 %>% 
  left_join(edu_exp_g7, by = c("location", "time")) %>% 
  left_join(gdexp_rnd_g7, by = c("location", "time")) %>% 
  left_join(infr_inv_g7, by = c("location", "time")) 

glimpse(productivity)
```

Trim data
```{r}
prod_uk_trim <- productivity %>% 
  filter(
    location == "GBR",
    time >= 1995 & time <=2019
  ) %>% 
  select(
    gdp_phw_usd, 
    gdexp_rnd_mil_usd, 
    rail_mil_eur, 
    road_mil_eur, 
    inland_mil_usd
  ) %>% 
  mutate(
    gdexp_rnd_bil_usd = gdexp_rnd_mil_usd / 1000, 
    rail_bil_eur = rail_mil_eur / 1000, 
    road_bil_eur = road_mil_eur / 1000, 
    inland_bil_usd = inland_mil_usd / 1000
  ) %>% 
  select(
    -gdexp_rnd_mil_usd, 
    -rail_mil_eur, 
    -road_mil_eur, 
    -inland_mil_usd
  )
```



Check for aliases
```{r}
alias(lm(gdp_phw_usd ~ ., data = prod_uk_trim))
```


Call libraries for linear regression modelling 
```{r}
library(GGally)
library(ggfortify)
library(modelr)
library(relaimpo)
library(caret)
library(leaps)
```


Check for correlations in data
```{r}
ggpairs(prod_uk_trim)
```
#################################################################################################################################

Simple linear regression

Response: gdp_phw_usd

Predictor: gdexp_rnd_bil_usd

```{r}
prod_uk_trim %>%
  ggplot(aes(x = gdexp_rnd_bil_usd, y = gdp_phw_usd)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

Goodness-of-fit diagnostics
```{r}
model_1 <- lm(gdp_phw_usd ~ gdexp_rnd_bil_usd, data = prod_uk_trim)

autoplot(model_1) #diagnostics
```

```{r}
summary(model_1)
```
#################################################################################################################################

- Adding a second predictor to the model

Calculate residuals
```{r}
prod_uk_remaining_resid <- prod_uk_trim %>%
  add_residuals(model_1) %>%
  select(-c("gdp_phw_usd", "gdexp_rnd_bil_usd"))

prod_uk_remaining_resid %>%
  ggpairs()
```

It seems that road_bil_eur is a good candidate for a second predictor followed by inland_bil_usd

#################################################################################################################################


Model with road_bil_eur (model_2a)
```{r}
model_2a <- lm(gdp_phw_usd ~ gdexp_rnd_bil_usd + road_bil_eur, data = prod_uk_trim)

autoplot(model_2a) #diagnostics
```

```{r}
summary(model_2a)
```
#################################################################################################################################

Model with inland_bil_usd (model_2b)
```{r}
model_2b <- lm(gdp_phw_usd ~ gdexp_rnd_bil_usd + inland_bil_usd, data = prod_uk_trim)

autoplot(model_2b) #diagnostics
```
```{r}
summary(model_2b)
```

Results indicate that model_2b performs slightly better than model_2a. We keep model_2b for further modelling.

#################################################################################################################################


- Adding a third predictor to the model

Calculate residuals
```{r}
prod_uk_remaining_resid <- prod_uk_trim %>%
  add_residuals(model_2a) %>%
  select(-c("gdp_phw_usd", "gdexp_rnd_bil_usd", "inland_bil_usd"))

prod_uk_remaining_resid %>%
  ggpairs()
```

It seems that road_bil_eur could be used as a third predictor

Model with added road_bil_eur (model_3a)
```{r}
model_3a <- lm(gdp_phw_usd ~ gdexp_rnd_bil_usd + inland_bil_usd + road_bil_eur, data = prod_uk_trim)

autoplot(model_3a) #diagnostics
```

```{r}
summary(model_3a)
```

It doesn't seem that road_bil_eur adds too much value in explaining the variability of the response.


#################################################################################################################################

Let's see if adding an interaction makes any improvement in our model.

Check for including in the model  potential interactions between predictors
```{r}
coplot(gdp_phw_usd ~ gdexp_rnd_bil_usd | inland_bil_usd,
       rows = 1,
       panel = function(x, y, ...){
         points(x, y)
         abline(lm(y ~ x), col = "blue")
       },
       data = prod_uk_trim)
```

Model with added road_bil_eur (model_3b)
```{r}
model_3b <- lm(gdp_phw_usd ~ gdexp_rnd_bil_usd + inland_bil_usd + gdexp_rnd_bil_usd:inland_bil_usd, data = prod_uk_trim)

autoplot(model_3b) #diagnostics
```

```{r}
summary(model_3b)
```

The intercept variance has increased. Run an ANOVA test to see if it is worth including an interaction term in the model

```{r}
anova(model_2b, model_3b)
```
The ANOVA tells us that including the interaction is significantly better than not doing so.


#################################################################################################################################

Checking of relative importance of model terms
```{r}
calc.relimp(model_3b, type = "lmg", rela = TRUE)

```


#################################################################################################################################
#################################################################################################################################

__K-fold cross validation__

```{r}
# set up options for train function below
cv_10_fold <- trainControl(method = "cv", # cross-validation
                           number = 10, # 10-fold
                           savePredictions = TRUE) # save all predictions

model_3b_kfold <- train(gdp_phw_usd ~ gdexp_rnd_bil_usd + inland_bil_usd + 
                 gdexp_rnd_bil_usd:inland_bil_usd,
               data = prod_uk_trim,
               trControl = cv_10_fold, # use options defined above
               method = 'lm')
```

```{r}
model_3b_kfold$resample
```



```{r}
tibble(
  relationship = "GDP_phw ~ RnD + Inland_inv + RnD:Inland_inv",
  RMSE = mean(model_3b_kfold$resample$RMSE),
  Rsquared = mean(model_3b_kfold$resample$Rsquared)
)
```




```{r}
model_2b_kfold <- train(gdp_phw_usd ~ gdexp_rnd_bil_usd + inland_bil_usd,
               data = prod_uk_trim,
               trControl = cv_10_fold, # use options defined above
               method = 'lm')
```


```{r}
model_2b_kfold$resample
```

```{r}
tibble(
  relationship = "GDP_phw ~ RnD + Inland_inv",
  RMSE = mean(model_2b_kfold$resample$RMSE),
  Rsquared = mean(model_2b_kfold$resample$Rsquared)
)
```


#################################################################################################################################
#################################################################################################################################


__Automated modelling__

```{r}
regsubsets_exhaustive <- regsubsets(gdp_phw_usd ~ ., data = prod_uk_trim, nvmax = 5, method = "exhaustive")
```

```{r}
sum_regsubsets_exhaustive <- summary(regsubsets_exhaustive)
sum_regsubsets_exhaustive
```


```{r}
plot(regsubsets_exhaustive, scale = "bic")
```


```{r}
plot(sum_regsubsets_exhaustive$bic, type = "b")
```



```{r}
plot(sum_regsubsets_exhaustive$rsq, type = "b")
```
















